---
title: "Stats141XP - Final Project (All)"
author: "Charles Liu (304804942)"
date: "4/30/2021"
output:
  html_document:
    df_print: paged
---

# Loading Necessary Packages
```{r, warning=FALSE, message=FALSE}
library(readr)
library(ggplot2)
library(tidyverse)
library(corrplot)
library(gplots)
library(ggpubr)
library(car)
```


# Loading Necessary Data
```{r, warning=FALSE, message=FALSE}
setwd(getwd())
d <- read_csv("Code_Sheet_Age_Project_Apr_26.csv")
```


# Setting up the data for the 3 AI Models
```{r}
diff_m1 <- d$age_actual - d$ai_model_1
diff_m2 <- d$age_actual - d$ai_model_2
diff_m3 <- d$age_actual - d$ai_model_3
```

## Histogram & Boxplots
```{r}
par(mfrow=c(2,2))
hist(diff_m1,breaks = 30, main="Model 1 Differences")
hist(diff_m2,breaks = 30, main="Model 2 Differences")
hist(diff_m3,breaks = 30, main="Model 3 Differences")

par(mfrow=c(1,1))
boxplot(diff_m1, diff_m2, diff_m3,
        main="Boxplot for All AI Model Differences", xlab="Model Types", 
        names=c("Model 1", "Model 2", "Model 3"))
# performs best -> Model 2 -> has some Outliers to consider and probably remove
# performs worst -> Model 1
# performs middle -> Model 3 -> has not Outliers, so might be better than M2

# We ignored Model 1 since it clearly performs the worst. Further analysis is unnecessary. M3 has both smaller Mean and Median than M2. We shall further determine which of the two models perform the best in terms of accuracy and reliability.
summary(diff_m2)
summary(diff_m3)
# needs to be closer to zero for better accuracy since they are all difference
```

**Comments:** Graphically, it looks like Model 2 performs better than Model 3 in terms of *Accuracy*. Numerically, Model 3 performs better than Model 2. Further analysis is needed for the AI Models.



# Accuracy & Reliability for All AI Models (both "pre" & "post")
## Set up the data
```{r}
# Differences in Age between Actual Age and AI Model Predicted Age
diff_m1 <- d$age_actual - d$ai_model_1
diff_m2 <- d$age_actual - d$ai_model_2
diff_m3 <- d$age_actual - d$ai_model_3

# Accuracy (using R-Squared)
all_r_m1 <- summary(lm(d$ai_model_1 ~ d$age_actual))$r.squared
all_r_m2 <- summary(lm(d$ai_model_2 ~ d$age_actual))$r.squared
all_r_m3 <- summary(lm(d$ai_model_3 ~ d$age_actual))$r.squared

# Accuracy (using MSE)
all_MSE_m1 <- mean((lm(d$age_actual ~ d$ai_model_1)$residuals)^2)
all_MSE_m2 <- mean((lm(d$age_actual ~ d$ai_model_2)$residuals)^2)
all_MSE_m3 <- mean((lm(d$age_actual ~ d$ai_model_3)$residuals)^2)

# Reliability (using correlation)
all_cor_m1 <- cor(d$age_actual, d$ai_model_1)
all_cor_m2 <- cor(d$age_actual, d$ai_model_2)
all_cor_m3 <- cor(d$age_actual, d$ai_model_3)

# Combine all above for comparisons
acc_reli_comparison_all_models <- 
  data.frame(`Model Type`=c("AI Model 1", "AI Model 2", "AI Model 3"),
             `Accuracy (using R-Squared)`=c(all_r_m1, all_r_m2, all_r_m3),
             `Accuracy (using MSE)`=c(all_MSE_m1,all_MSE_m2, all_MSE_m3),
             `Reliability (using correlation)`=c(all_cor_m1, all_cor_m2, 
                                                 all_cor_m3))
```

## Show the comparisons for each Models (Numerical)
```{r}
acc_reli_comparison_all_models
```
