---
title: "Stats141XP - Final Project (Cleaned)"
author: "Charles Liu (304804942)"
date: "4/30/2021"
output:
  html_document:
    df_print: paged
---

# Loading Necessary Packages
```{r, warning=FALSE, message=FALSE}
library(readr)
library(ggplot2)
library(tidyverse)
library(corrplot)
library(gplots)
library(ggpubr)
library(car)
library(psych)
```

# Loading Necessary Data
```{r, warning=FALSE, message=FALSE}
setwd(getwd())
d <- read_csv("Code_Sheet_Age_Project_Apr_26.csv")
```

# Set Up Work for Correlation
```{r}
# Set up conditions
all_pre_m1 <- sort(which(d$pre_or_post_operation %in% c("pre", "pre_2",
                                                        "pre_3")))
all_pre_m2 <- sort(which(d$pre_or_post_operation %in% c("pre", "pre_2",
                                                        "pre_3")))
all_pre_m3 <- sort(which(d$pre_or_post_operation %in% c("pre", "pre_2",
                                                        "pre_3")))
all_post_m1 <- sort(which(d$pre_or_post_operation %in% c("post", "post_2",
                                                        "post_3")))
all_post_m2 <- sort(which(d$pre_or_post_operation %in% c("post", "post_2",
                                                        "post_3")))
all_post_m3 <- sort(which(d$pre_or_post_operation %in% c("post", "post_2",
                                                        "post_3")))
pre1.2_pre_m1 <- sort(which(d$pre_or_post_operation %in% c("pre", "pre_2")))
pre1.2_pre_m2 <- sort(which(d$pre_or_post_operation %in% c("pre", "pre_2")))
pre1.2_pre_m3 <- sort(which(d$pre_or_post_operation %in% c("pre", "pre_2")))
post1.2_post_m1 <- sort(which(d$pre_or_post_operation %in% c("post", "post_2")))
post1.2_post_m2 <- sort(which(d$pre_or_post_operation %in% c("post", "post_2")))
post1.2_post_m3 <- sort(which(d$pre_or_post_operation %in% c("post", "post_2")))

# Apply the conditions
all_pre_actual_m1 <- d$age_actual[all_pre_m1]
all_pre_AIage_m1 <- d$ai_model_1[all_pre_m1]
all_pre_actual_m2 <- d$age_actual[all_pre_m2]
all_pre_AIage_m2 <- d$ai_model_2[all_pre_m2]
all_pre_actual_m3 <- d$age_actual[all_pre_m3]
all_pre_AIage_m3 <- d$ai_model_3[all_pre_m3]
all_post_actual_m1 <- d$age_actual[all_post_m1]
all_post_AIage_m1 <- d$ai_model_1[all_post_m1]
all_post_actual_m2 <- d$age_actual[all_post_m2]
all_post_AIage_m2 <- d$ai_model_2[all_post_m2]
all_post_actual_m3 <- d$age_actual[all_post_m3]
all_post_AIage_m3 <- d$ai_model_3[all_post_m3]
pre1.2_pre_actual_m1 <- d$age_actual[pre1.2_pre_m1]
pre1.2_pre_AIage_m1 <- d$ai_model_1[pre1.2_pre_m1]
pre1.2_pre_actual_m2 <- d$age_actual[pre1.2_pre_m2]
pre1.2_pre_AIage_m2 <- d$ai_model_2[pre1.2_pre_m2]
pre1.2_pre_actual_m3 <- d$age_actual[pre1.2_pre_m3]
pre1.2_pre_AIage_m3 <- d$ai_model_3[pre1.2_pre_m3]
post1.2_post_actual_m1 <- d$age_actual[post1.2_post_m1]
post1.2_post_AIage_m1 <- d$ai_model_1[post1.2_post_m1]
post1.2_post_actual_m2 <- d$age_actual[post1.2_post_m2]
post1.2_post_AIage_m2 <- d$ai_model_2[post1.2_post_m2]
post1.2_post_actual_m3 <- d$age_actual[post1.2_post_m3]
post1.2_post_AIage_m3 <- d$ai_model_3[post1.2_post_m3]

# Set up the Dataframes
all_pre_df <- data.frame(Actual=all_pre_actual_m1,
                         Model_1=all_pre_AIage_m1, 
                         Model_2=all_pre_AIage_m2, 
                         Model_3=all_pre_AIage_m3)
all_post_df <- data.frame(Actual=all_post_actual_m1,
                          Model_1=all_post_AIage_m1,
                          Model_2=all_post_AIage_m2,
                          Model_3=all_post_AIage_m3)
pre1.2_pre_df <- data.frame(Actual=pre1.2_pre_actual_m1,
                            Model_1=pre1.2_pre_AIage_m1,
                            Model_2=pre1.2_pre_AIage_m2, 
                            Model_3=pre1.2_pre_AIage_m3)
post1.2_post_df <- data.frame(Actual=post1.2_post_actual_m1,
                              Model_1=post1.2_post_AIage_m1,
                              Model_2=post1.2_post_AIage_m2,
                              Model_3=post1.2_post_AIage_m3)
both_df <- data.frame(Actual=d$age_actual,
                      Model_1=d$ai_model_1, 
                      Model_2=d$ai_model_2, 
                      Model_3=d$ai_model_3)
```


# Correlation Matrix (Reliability)
**Note:** All the Actuals for Each AI Models have the same Actual Ages.
```{r}
# All Pre-Measures
lowerCor(all_pre_df, method="pearson")

# All Post-Measures
lowerCor(all_post_df, method="pearson")

# Pre1 & Pre2
lowerCor(pre1.2_pre_df, method="pearson")

# Post1 & Post2
lowerCor(post1.2_post_df, method="pearson")

# Both Pre/Post-Measures (All Data)
lowerCor(both_df, method="pearson")
```

# Check Statistically Significant & Reproduciblity
1) P-value: how statistically significant they are (has to be lower than 0.05)
2) CI (Confidence Interval): This means that calculates 95% confidence intervals around the correlation value R. This means that if we repeated the experiment many times with datasets drawn from the same population the calculated confident intervals would contain the true value at 95% of the time these confidence intervals.
```{r}
# All Pre-Measures
corr.test(all_pre_df, use="pairwise.complete.obs")$ci[1:3,]

# All Post-Measures
corr.test(all_post_df, use="pairwise.complete.obs")$ci[1:3,]

# Pre1 & Pre2
corr.test(pre1.2_pre_df, use="pairwise.complete.obs")$ci[1:3,]

# Post1 & Post2
corr.test(post1.2_post_df, use="pairwise.complete.obs")$ci[1:3,]

# Both Pre/Post-Measures (All Data)
corr.test(both_df, use="pairwise.complete.obs")$ci[1:3,]
```

# Checking Reliability & Consistency
```{r, warning=FALSE, message=FALSE}
# Note: $alpha == splitHalf(...)[8] == "Average split half reliability"

# All Pre-Measures
alpha(all_pre_df)[3] # (? > 0.80 -> reliable)
splitHalf(all_pre_df)[8] # shows consistency (? > 0.80 -> consistent)

# All Post-Measures
alpha(all_post_df)[3] # (? > 0.80 -> reliable)
splitHalf(all_post_df)[8] # shows consistency (? > 0.80 -> consistent)

# Pre1 & Pre2
alpha(pre1.2_pre_df)[3] # (? > 0.80 -> reliable)
splitHalf(pre1.2_pre_df)[8] # shows consistency (? > 0.80 -> consistent)

# Post1 & Post2
alpha(post1.2_post_df)[3] # (? > 0.80 -> reliable)
splitHalf(post1.2_post_df)[8] # shows consistency (? > 0.80 -> consistent)

# Both Pre/Post-Measures (All Data)
alpha(both_df)[3] # (? > 0.80 -> reliable)
splitHalf(both_df)[8] # shows consistency (? > 0.80 -> consistent)
```