---
title: "Stats141XP - Final Project (All)"
author: "Charles Liu (304804942)"
date: "4/30/2021"
output:
  html_document:
    df_print: paged
---

# Loading Necessary Packages
```{r, warning=FALSE, message=FALSE}
library(readr)
library(ggplot2)
library(tidyverse)
library(corrplot)
library(gplots)
library(ggpubr)
library(car)
```


# Loading Necessary Data
```{r, warning=FALSE, message=FALSE}
setwd(getwd())
d <- read_csv("Code_Sheet_Age_Project_Apr_26.csv")
```


# Preliminary Analysis
```{r}
# Check for any NA's
anyNA(d) # No NA's

# Find which columns have NA's
colnames(d)[colSums(is.na(d)) > 0] # No NA's
summary(d)
glimpse(d)

# Edit `Upper bleph (0 = null, 1 = right, 2 = left, 3 = bilateral)` into character column
d$`Upper bleph (0 = null, 1 = right, 2 = left, 3 = bilateral)` <- as.character(d$`Upper bleph (0 = null, 1 = right, 2 = left, 3 = bilateral)`)

# Names of Numeric columns
d_num <- d %>% 
  select_if(is.numeric)
colnames(d_num)
d_num

# Names of Character columns
d_char <- d %>% 
  select_if(is.character)
colnames(d_char)
d_char
```


# Start Analyzing the Data (Numeric Columns)
```{r}
# Analyzing the Numeric columns
corr_d.1 <- cor(d_num[,1:5])
corrplot(corr_d.1, method = "circle") # smaller parts

corr_d.2 <- cor(d_num[,7:10])
corrplot(corr_d.2, method = "circle") # smaller parts

corr_d.3 <- cor(d_num[,11:14])
corrplot(corr_d.3, method = "circle") # smaller parts

corr_d.4 <- cor(d_num)
corrplot(corr_d.4, method = "circle") # combined
```


# Setting up the data for the 3 AI Models
```{r}
diff_m1 <- d$age_actual - d$ai_model_1
diff_m2 <- d$age_actual - d$ai_model_2
diff_m3 <- d$age_actual - d$ai_model_3
```

## Histogram & Boxplots
```{r}
par(mfrow=c(2,2))
hist(diff_m1,breaks = 30, main="Model 1 Differences")
hist(diff_m2,breaks = 30, main="Model 2 Differences")
hist(diff_m3,breaks = 30, main="Model 3 Differences")

par(mfrow=c(1,1))
boxplot(diff_m1, diff_m2, diff_m3,
        main="Boxplot for All AI Model Differences", xlab="Model Types", 
        names=c("Model 1", "Model 2", "Model 3"))
# performs best -> Model 2 -> has some Outliers to consider and probably remove
# performs worst -> Model 1
# performs middle -> Model 3 -> has not Outliers, so might be better than M2

# We ignored Model 1 since it clearly performs the worst. Further analysis is unnecessary. M3 has both smaller Mean and Median than M2. We shall further determine which of the two models perform the best in terms of accuracy and reliability. (Should look at MSE to tell for accuracy)
summary(diff_m2)
summary(diff_m3)
```

**Comments:** Graphically, it looks like Model 2 performs better than Model 3 in terms of *Accuracy*. Numerically, Model 3 performs better than Model 2. Further analysis is needed for the AI Models.



# Accuracy & Reliability for All AI Models (both "pre" & "post")
## Set up the data
```{r}
# Differences in Age between Actual Age and AI Model Predicted Age
diff_m1 <- d$age_actual - d$ai_model_1
diff_m2 <- d$age_actual - d$ai_model_2
diff_m3 <- d$age_actual - d$ai_model_3

# Accuracy (using R-Squared)
all_r_m1 <- summary(lm(d$ai_model_1 ~ d$age_actual))$r.squared
all_r_m2 <- summary(lm(d$ai_model_2 ~ d$age_actual))$r.squared
all_r_m3 <- summary(lm(d$ai_model_3 ~ d$age_actual))$r.squared

# Accuracy (using MSE)
all_MSE_m1 <- mean((lm(d$age_actual ~ d$ai_model_1)$residuals)^2)
all_MSE_m2 <- mean((lm(d$age_actual ~ d$ai_model_2)$residuals)^2)
all_MSE_m3 <- mean((lm(d$age_actual ~ d$ai_model_3)$residuals)^2)

# Reliability (using correlation)
all_cor_m1 <- cor(d$age_actual, d$ai_model_1)
all_cor_m2 <- cor(d$age_actual, d$ai_model_2)
all_cor_m3 <- cor(d$age_actual, d$ai_model_3)

# Combine all above for comparisons
acc_reli_comparison_all_models <- 
  data.frame(`Model Type`=c("AI Model 1", "AI Model 2", "AI Model 3"),
             `Accuracy (using R-Squared)`=c(all_r_m1, all_r_m2, all_r_m3),
             `Accuracy (using MSE)`=c(all_MSE_m1,all_MSE_m2, all_MSE_m3),
             `Reliability (using correlation)`=c(all_cor_m1, all_cor_m2, 
                                                 all_cor_m3))
```

## Show the comparisons for each Models (Numerical)
```{r}
acc_reli_comparison_all_models
```



## Plot Means for Categorical Variables [Model 2]

**NOTE:** When it comes to the Categorical variables for "f-number" all the way till "dimensions" (along with "Upper Bleph"), they are all "Null", but the rest of the information might be useful. (columns 11,21-27) (observations 82 & 113 are all Null for these columns)

```{r, warning=FALSE, message=FALSE}
par(mfrow=c(2,2))
plotmeans(diff_m2[-c(53,82,113)] ~ d$model[-c(53,82,113)], 
          data = d, xlab="Camera Model", 
          ylab="Age Difference (M2)", main="Mean Significance for Camera Model") # need to remove iPhone 6 and Null -> I removed iPhone 6 (since it was n=1 and it is observation 53) but might be important -> further analysis needed

plotmeans(diff_m2[-c(82,113)] ~ d$make[-c(82,113)], 
          data = d, xlab="Camera Type", 
          ylab="Age Difference (M2)", main="Mean Significance for Camera Type") # not as relevant since mostly Canon anyways but might be interested in

plotmeans(diff_m2[-c(82,113)] ~ d$sensitivity[-c(82,113)], 
          data = d, xlab="Sensitivity Rating", 
          ylab="Age Difference (M2)", main="Mean Significance for Sensitivity Rating")

plotmeans(diff_m2[-c(82,113)] ~ d$`exposure time`[-c(82,113)], 
          data = d, xlab="Exposure Time", 
          ylab="Age Difference (M2)", main="Mean Significance for Exposure Time") # need to edit to either remove the n = 1 observations or keep them -> further analysis is needed

par(mfrow=c(2,2))
plotmeans(diff_m2[-c(82,113)] ~ d$`focal length`[-c(82,113)], 
          data = d, xlab="Focal Length", 
          ylab="Age Difference (M2)", main="Mean Significance for Focal Length") # need to edit to either remove the n = 1 observations or keep them -> further analysis is needed

plotmeans(diff_m2[-c(82,113)] ~ d$`f-number`[-c(82,113)], 
          data = d, xlab="F-Number", 
          ylab="Age Difference (M2)", main="Mean Significance for F-Number") # n = 1 is really dragging down the Plot Means -> further analysis is needed

plotmeans(diff_m2[-c(82,113)] ~ d$dimensions[-c(82,113)], 
          data = d, xlab="Dimensions of Photo", main="Mean Significance for Dimensions") # need to edit to either remove the n = 1 observations or keep them -> further analysis is needed

plotmeans(diff_m2[-c(82,113)] ~ d$`Upper bleph (0 = null, 1 = right, 2 = left, 3 = bilateral)`[-c(82,113)], 
          data = d, xlab="Upper Bleph Treatment", 
          ylab="Age Difference (M2)", main="Mean Significance for Upper Bleph")
```


## Plot Means for Categorical Variables [Model 3]

**NOTE:** When it comes to the Categorical variables for "f-number" all the way till "dimensions" (along with "Upper Bleph"), they are all "Null", but the rest of the information might be useful. (columns 11,21-27) (observations 82 & 113 are all Null for these columns)

```{r, warning=FALSE, message=FALSE}
par(mfrow=c(2,2))
plotmeans(diff_m3[-c(53,82,113)] ~ d$model[-c(53,82,113)], 
          data = d, xlab="Camera Model", 
          ylab="Age Difference (M3)", main="Mean Significance for Camera Model") # need to remove iPhone 6 and Null -> I removed iPhone 6 (since it was n=1 and it is observation 53) but might be important -> further analysis needed

plotmeans(diff_m3[-c(82,113)] ~ d$make[-c(82,113)], 
          data = d, xlab="Camera Type", 
          ylab="Age Difference (M3)", main="Mean Significance for Camera Type") # not as relevant since mostly Canon anyways but might be interested in

plotmeans(diff_m3[-c(82,113)] ~ d$sensitivity[-c(82,113)], 
          data = d, xlab="Sensitivity Rating", 
          ylab="Age Difference (M3)", main="Mean Significance for Sensitivity Rating")

plotmeans(diff_m3[-c(82,113)] ~ d$`exposure time`[-c(82,113)], 
          data = d, xlab="Exposure Time", 
          ylab="Age Difference (M3)", main="Mean Significance for Exposure Time") # need to edit to either remove the n = 1 observations or keep them -> further analysis is needed

par(mfrow=c(2,2))
plotmeans(diff_m3[-c(82,113)] ~ d$`focal length`[-c(82,113)], 
          data = d, xlab="Focal Length", 
          ylab="Age Difference (M3)", main="Mean Significance for Focal Length") # need to edit to either remove the n = 1 observations or keep them -> further analysis is needed

plotmeans(diff_m3[-c(82,113)] ~ d$`f-number`[-c(82,113)], 
          data = d, xlab="F-Number", 
          ylab="Age Difference (M3)", main="Mean Significance for F-Number") # n = 1 is really dragging down the Plot Means -> further analysis is needed

plotmeans(diff_m3[-c(82,113)] ~ d$dimensions[-c(82,113)], 
          data = d, xlab="Dimensions of Photo", 
          ylab="Age Difference (M3)", main="Mean Significance for Dimensions") # need to edit to either remove the n = 1 observations or keep them -> further analysis is needed

plotmeans(diff_m3[-c(82,113)] ~ d$`Upper bleph (0 = null, 1 = right, 2 = left, 3 = bilateral)`[-c(82,113)], 
          data = d, xlab="Upper Bleph Treatment", 
          ylab="Age Difference (M3)", main="Mean Significance for Upper Bleph")
```


## Create Age Difference Plot for Each Models (Scatterplot)
```{r}
par(mfrow=c(2,2))
# Model 1
plot(d$age_actual,diff_m1,xlab = "Actual Age",main = "Difference vs Age Group (Model 1)",ylab = "Age Difference")
lines(c(31,85),c(3.023,-4.91),col = "red",lwd = 3)

# Model 2
plot(d$age_actual,diff_m2,xlab = "Actual Age",main = "Difference vs Age Group (Model 2)",ylab = "Age Difference")
lines(c(31,85),c(3.023,-4.91),col = "red",lwd = 3)

# Model 3
plot(d$age_actual,diff_m3,xlab = "Actual Age",main = "Difference vs Age Group (Model 3)",ylab = "Age Difference")
lines(c(31,85),c(3.023,-4.91),col = "red",lwd = 3)
```



# Testing Reliability for ALL Combinations of "pre-measurements" [AI Model 1]

**NOTE:** The parts are as follows...
  i) "pre" & "pre_2" are Parts 1.1 - 6.1
  ii) "pre" & "pre_3" are Parts 7.1 - 11.1
  iii) "pre_2" & "pre_3" are Parts 12.1 - 16.1
  iv) Every "pre-measurement" are Parts 17.1 - 21.1

## Analysis (Part 1.1)
```{r}
## Re-order the dataset
nrow(d)
for (i in 1:301) {
  if(d$patient_name[i] %in% d$patient_name[i+1])
  {
    if(d$pre_or_post_operation[i] %in% "pre_2" &&
       d$pre_or_post_operation[i+1] %in% "pre")
    {
      temp <- d[i,]
      d[i,] <- d[i+1,]
      d[i+1,] <- temp
    }
  }
}
```

## Analysis (Part 2.1)
```{r, warning=FALSE, message=FALSE}
age11_m1 <- which(d$pre_or_post_operation %in% "pre")
age2_m1 <- which(d$pre_or_post_operation %in% "pre_2")
age3_m1 <- which(d$pre_or_post_operation %in% "pre_3")
all_pre_m1 <- sort(c(age11_m1, age2_m1 ,age3_m1))
age1_m1 <- age2_m1 - 1

age2_pre_m1 <- d$ai_model_1[age2_m1]
age1_pre_m1 <- d$ai_model_1[age1_m1]
age3_pre_m1 <- d$ai_model_1[age3_m1]
pre1.2_diff_m1 <- d$age_actual[age2_m1] - d$age_actual[age1_m1]
hist(pre1.2_diff_m1)
```

## Analysis (Part 3.1)
```{r}
## Compute the coefficient of correlation of two predicted age for "pre" & "pre_2" for AI M1
all_pre1.2_index_m1 <- sort(c(age1_m1, age2_m1))
length(all_pre1.2_index_m1)/2
AIage_pre_m1 <- numeric(57)
AIage_pre2_m1 <- numeric(57)
for (i in 1:57) {
  temp <- i * 2 -1
  if(d$age_actual[all_pre1.2_index_m1[temp]] > 
     d$age_actual[all_pre1.2_index_m1[temp + 1]])
  {
    AIage_pre_m1[i] <- d$ai_model_1[all_pre1.2_index_m1[temp + 1]]
    AIage_pre2_m1[i] <- d$ai_model_1[all_pre1.2_index_m1[temp]]
  }
  else{
    AIage_pre_m1[i] <- d$ai_model_1[all_pre1.2_index_m1[temp]]
    AIage_pre2_m1[i] <- d$ai_model_1[all_pre1.2_index_m1[temp + 1]]
  }
}
```

## Analysis (Part 4.1)
```{r}
pre1.2_age_mx_m1 <- cbind(pre1.2_diff_m1, age2_pre_m1 - age1_pre_m1)
pre1.2_age_mx_m1 # might be better to look at head(...) and tail(...)
# Make subgroups for time
## Over Half Years & Over Full Years
time1_age_m1 <- c(which(pre1.2_diff_m1 > 0.5),
                    which(pre1.2_diff_m1 < -0.5))
time1_age_m1 <- sort(time1_age_m1)

time2_age_m1 <- which(pre1.2_diff_m1 >= -1 & 
              pre1.2_diff_m1 <= 1)
time2_age_m1 <- sort(time2_age_m1)

time3_age_m1 <- c(which(pre1.2_diff_m1 < -1),
        which(pre1.2_diff_m1 > 1))
time3_age_m1 <- sort(time3_age_m1)

# Correlations
cor1_m1 <- cor(AIage_pre_m1, AIage_pre2_m1)
cor2_m1 <- cor(AIage_pre_m1[time1_age_m1], AIage_pre2_m1[time1_age_m1])
cor3_m1 <- cor(AIage_pre_m1[time2_age_m1], AIage_pre2_m1[time2_age_m1])
cor4_m1 <- cor(AIage_pre_m1[time3_age_m1], AIage_pre2_m1[time3_age_m1])

pre1.2_cor_mx_m1 <- data.frame(Correlation=c(cor1_m1, cor2_m1, 
                                             cor3_m1, cor4_m1),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
pre1.2_cor_mx_m1
```

## Analysis (Part 5.1)
```{r}
AIage_m1_m1 <- lm(AIage_pre_m1 ~ AIage_pre2_m1)
ip_m1_m1 <- influencePlot(AIage_m1_m1)
ip_m1_m1
4/length(AIage_pre_m1) # Hat-values limit for Influcence Plot
# High Leverage Points: 51, 56 (? > 4/n for Hat-values)
# Outlier Points: 8, 40, 51(StudRes is either [-2 > ? > +2])
# Good Leverage Points: 56 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: 51 (? > 4/n for Hat values & outside [-2 > ? > +2])
lev_m1_m1 <- d[which(d$pre_or_post_operation %in% c("pre_2")),]
lev_m1_m1[51, 6:8] # (might remove this Bad Leverage)
# We'll see what happens when we remove the Bad Leverage...
```

## Analysis (Part 6.1)
```{r}
# Finding the Correlation Cofficients for "pre" & "pre_2" for AI M1
pre1.2_cor_improved_m1 <- cor(age1_pre_m1[-c(51)], age2_pre_m1[-c(51)])
pre1.2_cor_old_m1 <- cor(age1_pre_m1, age2_pre_m1)

pre1.2_cor_compare_m1 <- data.frame(Correlation=c(pre1.2_cor_old_m1,
                                           pre1.2_cor_improved_m1),
                             Type=c("All Points", "Removed Bad Leverages"))
pre1.2_cor_compare_m1 # Removing the Bad Leverage Points (points 51) improves the reliability

# Run the Linear Regression
pre1.2_all_m1_m1 <- lm(age1_pre_m1 ~ age2_pre_m1)
summary(pre1.2_all_m1_m1)

pre1.2_improved_m1_m1 <- lm(age1_pre_m1[-c(51)] ~ age2_pre_m1[-c(51)])
summary(pre1.2_improved_m1_m1)

pre1.2_r_compare_m1 <- data.frame(R_sq=c(summary(pre1.2_all_m1_m1)$r.squared, 
                  summary(pre1.2_improved_m1_m1)$r.squared),
                             Type=c("All Points", "Removed Bad Leverages")) 
pre1.2_r_compare_m1 # R-Squared improved

# Conclusion: It might be better to remove the Bad Leverage Point 51 for Model 1. By observation, it approcimately was off by 13 years. This is for comparing "pre" and "pre_2" ONLY!
lev_m1_m1[51, 6:8]
as.numeric(lev_m1_m1[51, 8] - lev_m1_m1[51, 7]) # How much it was off by
```

## Analysis (Part 7.1)
```{r}
# Set up data for "pre" & "pre_3" for AI M1
pre1.3_m1 <- age3_m1 - 2
pre1.3_df <- d[sort(c(pre1.3_m1, age3_m1)),]
pre1_m1 <- which(pre1.3_df$pre_or_post_operation %in% "pre")
pre3_m1 <- which(pre1.3_df$pre_or_post_operation %in% "pre_3")

# Note: Last year's messed up and had c(1,3,5,7,9,11,14,16,18) -> "pre", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "pre_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
pre1_df_m1 <- pre1.3_df[pre1_m1,]
pre3_df_m1 <- pre1.3_df[pre3_m1,]
```

## Analysis (Part 8.1)
```{r}
pre1.3_diff_m1 <- pre3_df_m1$age_actual - pre1_df_m1$age_actual
pre1_AIage_m1 <- pre1_df_m1$ai_model_1
pre3_AIage_m1 <- pre3_df_m1$ai_model_1
hist(pre1.3_diff_m1)
```

## Analysis (Part 9.1)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time4_age_m1 <- c(which(pre1.3_diff_m1 > 0.5),
                    which(pre1.3_diff_m1 < -0.5))
time4_age_m1 <- sort(time4_age_m1)

time5_age_m1 <- which(pre1.3_diff_m1 >= -1 & 
              pre1.3_diff_m1 <= 1)
time5_age_m1 <- sort(time5_age_m1)

time6_age_m1 <- c(which(pre1.3_diff_m1 < -1),
        which(pre1.3_diff_m1 > 1))
time6_age_m1 <- sort(time6_age_m1)

# Correlations
cor5_m1 <- cor(pre1_AIage_m1, pre3_AIage_m1)
cor6_m1 <- cor(pre1_AIage_m1[time4_age_m1], pre3_AIage_m1[time4_age_m1])
cor7_m1 <- cor(pre1_AIage_m1[time5_age_m1], pre3_AIage_m1[time5_age_m1])
cor8_m1 <- cor(pre1_AIage_m1[time6_age_m1], pre3_AIage_m1[time6_age_m1])

pre1.3_cor_mx_m1 <- data.frame(Correlation=c(cor5_m1, cor6_m1, 
                                             cor7_m1, cor8_m1),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
pre1.3_cor_mx_m1
```

## Analysis (Part 10.1)
```{r}
AIage_m2_m1 <- lm(pre1_AIage_m1 ~ pre3_AIage_m1)
ip_m2_m1 <- influencePlot(AIage_m2_m1)
ip_m2_m1
4/length(pre3_AIage_m1) # Hat-values limit for Influcence Plot
# High Leverage Points: 4 (? > 4/n for Hat-values)
# Outlier Points: 2 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 4 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 11.1)
```{r}
# Finding the Correlation Cofficients for "pre" & "pre_3" for AI M1
pre1.3_cor_old_m1 <- cor(pre1_AIage_m1, pre3_AIage_m1)

pre1.3_cor_compare_m1 <- data.frame(Correlation=c(pre1.3_cor_old_m1),
                             Type=c("All Points"))
pre1.3_cor_compare_m1 # No Bad Leverage Points

# Run the Linear Regression
pre1.3_all_m1_m1 <- lm(pre1_AIage_m1 ~ pre3_AIage_m1)
summary(pre1.3_all_m1_m1)

pre1.3_r_compare_m1 <- data.frame(R_sq=c(summary(pre1.3_all_m1_m1)$r.squared),
                             Type=c("All Points")) 
pre1.3_r_compare_m1 # No Bad Leverage Points
```

## Analysis (Part 12.1)
```{r}
# Set up data for "pre_2" & "pre_3" for AI M1
pre2.3_m1 <- age3_m1 - 1
pre2.3_df <- d[sort(c(pre2.3_m1, age3_m1)),]
pre2_m1 <- which(pre2.3_df$pre_or_post_operation %in% "pre_2")
pre3_m1 <- which(pre2.3_df$pre_or_post_operation %in% "pre_3")

# Note: Last year's messed up and had c(1,3,5,7,10,11,14,16,18) -> "pre_2", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "pre_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
pre2_df_m1 <- pre2.3_df[pre2_m1,] 
pre3_df_m1 <- pre2.3_df[pre3_m1,]
```

## Analysis (Part 13.1)
```{r}
pre2.3_diff_m1 <- pre3_df_m1$age_actual - pre2_df_m1$age_actual
pre2_AIage_m1 <- pre2_df_m1$ai_model_1
pre3_AIage_m1 <- pre3_df_m1$ai_model_1
hist(pre2.3_diff_m1)
```

## Analysis (Part 14.1)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time7_age_m1 <- c(which(pre2.3_diff_m1 > 0.5),
                    which(pre2.3_diff_m1 < -0.5))
time7_age_m1 <- sort(time7_age_m1)

time8_age_m1 <- which(pre2.3_diff_m1 >= -1 & 
              pre2.3_diff_m1 <= 1)
time8_age_m1 <- sort(time8_age_m1)

time9_age_m1 <- c(which(pre2.3_diff_m1 < -1),
        which(pre2.3_diff_m1 > 1))
time9_age_m1 <- sort(time9_age_m1)

# Correlations
cor9_m1 <- cor(pre2_AIage_m1, pre3_AIage_m1)
cor10_m1 <- cor(pre2_AIage_m1[time7_age_m1], pre3_AIage_m1[time7_age_m1])
cor11_m1 <- cor(pre2_AIage_m1[time8_age_m1], pre3_AIage_m1[time8_age_m1])
cor12_m1 <- cor(pre2_AIage_m1[time9_age_m1], pre3_AIage_m1[time9_age_m1])

pre2.3_cor_mx_m1 <- data.frame(Correlation=c(cor9_m1, cor10_m1, 
                                             cor11_m1, cor12_m1),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
pre2.3_cor_mx_m1 # We have N/A since either one or no points for the time given
```

## Analysis (Part 15.1)
```{r}
AIage_m3_m1 <- lm(pre2_AIage_m1 ~ pre3_AIage_m1)
ip_m3_m1 <- influencePlot(AIage_m3_m1)
ip_m3_m1
4/length(pre2_AIage_m1) # Hat-values limit for Influcence Plot
# High Leverage Points: 4 (? > 4/n for Hat-values)
# Outlier Points: 1 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 4 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 16.1)
```{r}
# Finding the Correlation Cofficients for "pre_2" & "pre_3" for AI M1
pre2.3_cor_old_m1 <- cor(pre2_AIage_m1, pre3_AIage_m1)

pre2.3_cor_compare_m1 <- data.frame(Correlation=c(pre2.3_cor_old_m1),
                             Type=c("All Points"))
pre2.3_cor_compare_m1 # No Bag Leverage Points

# Run the Linear Regression
pre2.3_all_m1_m1 <- lm(pre2_AIage_m1 ~ pre3_AIage_m1)
summary(pre2.3_all_m1_m1)

pre2.3_r_compare_m1 <- data.frame(R_sq=c(summary(pre2.3_all_m1_m1)$r.squared),
                             Type=c("All Points")) 
pre2.3_r_compare_m1 # No Bad Leverage Points
```

## Analysis (Part 17.1)
```{r, warning=FALSE, message=FALSE}
every_pre_m1 <- sort(which(d$pre_or_post_operation %in% c("pre", "pre_2",
                                                        "pre_3")))
every_pre_diff_m1 <- d$age_actual[every_pre_m1] - d$ai_model_1[every_pre_m1]
hist(every_pre_diff_m1)
```

## Analysis (Part 18.1)
```{r}
every_pre_actual_m1 <- d$age_actual[every_pre_m1]
every_pre_AIage_m1 <- d$ai_model_1[every_pre_m1]
```

## Analysis (19.1)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time10_age_m1 <- c(which(every_pre_diff_m1 > 0.5),
                    which(every_pre_diff_m1 < -0.5))
time10_age_m1 <- sort(time10_age_m1)

time11_age_m1 <- which(every_pre_diff_m1 >= -1 & 
              every_pre_diff_m1 <= 1)
time11_age_m1 <- sort(time11_age_m1)

time12_age_m1 <- c(which(every_pre_diff_m1 < -1),
        which(every_pre_diff_m1 > 1))
time12_age_m1 <- sort(time12_age_m1)

# Correlations
cor13_m1 <- cor(every_pre_AIage_m1, 
                every_pre_actual_m1)
cor14_m1 <- cor(every_pre_AIage_m1[time10_age_m1],
                every_pre_actual_m1[time10_age_m1])
cor15_m1 <- cor(every_pre_AIage_m1[time11_age_m1],
                every_pre_actual_m1[time11_age_m1])
cor16_m1 <- cor(every_pre_AIage_m1[time12_age_m1],
                every_pre_actual_m1[time12_age_m1])

every_pre_cor_mx_m1 <- data.frame(Correlation=c(cor13_m1, cor14_m1, 
                                             cor15_m1, cor16_m1),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
every_pre_cor_mx_m1
```

## Analysis (Part 20.1)
```{r}
AIage_m4_m1 <- lm(every_pre_AIage_m1 ~ 
                            every_pre_actual_m1)
ip_m4_m1 <- influencePlot(AIage_m4_m1)
ip_m4_m1
4/length(every_pre_actual_m1) # Hat-values limit for Influcence Plot
# High Leverage Points: 35, 165 (? > 4/n for Hat-values)
# Outlier Points: 100, 166 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 35, 165 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2]
```

## Analysis (Part 21.1)
```{r}
# Finding the Correlation Cofficients for ALL "pre-measures" for AI M1
every_pre_cor_old_m1 <- cor(every_pre_AIage_m1, 
                            every_pre_actual_m1)

every_pre_cor_compare_m1 <- data.frame(Correlation=c(every_pre_cor_old_m1),
                             Type=c("All Points"))
every_pre_cor_compare_m1 # No Bad Leverage Points

# Run the Linear Regression
every_all_pre_m1_m1 <- lm(every_pre_AIage_m1 ~
                                 every_pre_actual_m1)
summary(every_all_pre_m1_m1)

every_all_pre_r_compare_m1 <- data.frame(R_sq=c(summary(every_all_pre_m1_m1)$r.squared),
                             Type=c("All Points")) 
every_all_pre_r_compare_m1 # No Bad Leverage Points
```



# Testing Reliability for ALL Combinations of "pre-measurements" [AI Model 2]

**NOTE:** The parts are as follows...
  i) "pre" & "pre_2" are Parts 1.2 - 6.2
  ii) "pre" & "pre_3" are Parts 7.2 - 11.2
  iii) "pre_2" & "pre_3" are Parts 12.2 - 16.2
  iv) Every "pre-measurement" are Parts 17.2 - 21.2

## Analysis (Part 1.2)
```{r}
## Re-order the dataset
nrow(d)
for (i in 1:301) {
  if(d$patient_name[i] %in% d$patient_name[i+1])
  {
    if(d$pre_or_post_operation[i] %in% "pre_2" &&
       d$pre_or_post_operation[i+1] %in% "pre")
    {
      temp <- d[i,]
      d[i,] <- d[i+1,]
      d[i+1,] <- temp
    }
  }
}
```

## Analysis (Part 2.2)
```{r, warning=FALSE, message=FALSE}
age11_m2 <- which(d$pre_or_post_operation %in% "pre")
age2_m2 <- which(d$pre_or_post_operation %in% "pre_2")
age3_m2 <- which(d$pre_or_post_operation %in% "pre_3")
all_pre_m2 <- sort(c(age11_m2, age2_m2 ,age3_m2))
age1_m2 <- age2_m2 - 1

age2_pre_m2 <- d$ai_model_2[age2_m2]
age1_pre_m2 <- d$ai_model_2[age1_m2]
age3_pre_m2 <- d$ai_model_2[age3_m2]
pre1.2_diff_m2 <- d$age_actual[age2_m2] - d$age_actual[age1_m2]
hist(pre1.2_diff_m2)
```

## Analysis (Part 3.2)
```{r}
## Compute the coefficient of correlation of two predicted age for "pre" & "pre_2" for AI M2
all_pre1.2_index_m2 <- sort(c(age1_m2, age2_m2))
length(all_pre1.2_index_m2)/2
AIage_pre_m2 <- numeric(57)
AIage_pre2_m2 <- numeric(57)
for (i in 1:57) {
  temp <- i * 2 -1
  if(d$age_actual[all_pre1.2_index_m2[temp]] > 
     d$age_actual[all_pre1.2_index_m2[temp + 1]])
  {
    AIage_pre_m2[i] <- d$ai_model_2[all_pre1.2_index_m2[temp + 1]]
    AIage_pre2_m2[i] <- d$ai_model_2[all_pre1.2_index_m2[temp]]
  }
  else{
    AIage_pre_m2[i] <- d$ai_model_2[all_pre1.2_index_m2[temp]]
    AIage_pre2_m2[i] <- d$ai_model_2[all_pre1.2_index_m2[temp + 1]]
  }
}
```

## Analysis (Part 4.2)
```{r}
pre1.2_age_mx_m2 <- cbind(pre1.2_diff_m2, age2_pre_m2 - age1_pre_m2)
pre1.2_age_mx_m2 # might be better to look at head(...) and tail(...)
# Make subgroups for time
## Over Half Years & Over Full Years
time1_age_m2 <- c(which(pre1.2_diff_m2 > 0.5),
                    which(pre1.2_diff_m2 < -0.5))
time1_age_m2 <- sort(time1_age_m2)

time2_age_m2 <- which(pre1.2_diff_m2 >= -1 & 
              pre1.2_diff_m2 <= 1)
time2_age_m2 <- sort(time2_age_m2)

time3_age_m2 <- c(which(pre1.2_diff_m2 < -1),
        which(pre1.2_diff_m2 > 1))
time3_age_m2 <- sort(time3_age_m2)

# Correlations
cor1_m2 <- cor(AIage_pre_m2, AIage_pre2_m2)
cor2_m2 <- cor(AIage_pre_m2[time1_age_m2], AIage_pre2_m2[time1_age_m2])
cor3_m2 <- cor(AIage_pre_m2[time2_age_m2], AIage_pre2_m2[time2_age_m2])
cor4_m2 <- cor(AIage_pre_m2[time3_age_m2], AIage_pre2_m2[time3_age_m2])

pre1.2_cor_mx_m2 <- data.frame(Correlation=c(cor1_m2, cor2_m2, 
                                             cor3_m2, cor4_m2),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
pre1.2_cor_mx_m2
```

## Analysis (Part 5.2)
```{r}
AIage_m1_m2 <- lm(AIage_pre_m2 ~ AIage_pre2_m2)
ip_m1_m2 <- influencePlot(AIage_m1_m2)
ip_m1_m2
4/length(AIage_pre_m2) # Hat-values limit for Influcence Plot
# High Leverage Points: 22, 51, 56 (? > 4/n for Hat-values)
# Outlier Points: 19, 56 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 22, 51 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: 56 (? > 4/n for Hat values & outside [-2 > ? > +2])
lev_m1_m2 <- d[which(d$pre_or_post_operation %in% c("pre_2")),]
lev_m1_m2[56, c(6,7,9)] # (might remove this Bad Leverage)
# We'll see what happens when we remove the Bad Leverage...
```

## Analysis (Part 6.2)
```{r}
# Finding the Correlation Cofficients for "pre" & "pre_2" for AI M2
pre1.2_cor_improved_m2 <- cor(age1_pre_m2[-c(56)], age2_pre_m2[-c(56)])
pre1.2_cor_old_m2 <- cor(age1_pre_m2, age2_pre_m2)

pre1.2_cor_compare_m2 <- data.frame(Correlation=c(pre1.2_cor_old_m2,
                                           pre1.2_cor_improved_m2),
                             Type=c("All Points", "Removed Bad Leverages"))
pre1.2_cor_compare_m2 # Removing the Bad Leverage Points (points 56) decreases the reliability by a very small amount

# Run the Linear Regression
pre1.2_all_m1_m2 <- lm(age1_pre_m2 ~ age2_pre_m2)
summary(pre1.2_all_m1_m2)

pre1.2_improved_m1_m2 <- lm(age1_pre_m2[-c(56)] ~ age2_pre_m2[-c(56)])
summary(pre1.2_improved_m1_m2) 

pre1.2_r_compare_m2 <- data.frame(R_sq=c(summary(pre1.2_all_m1_m2)$r.squared, 
                  summary(pre1.2_improved_m1_m2)$r.squared),
                             Type=c("All Points", "Removed Bad Leverages")) 
pre1.2_r_compare_m2 # R-Squared slightly decreased

# Conclusion: It might be best to keep the Bad Leverage Point 56 for Model 2. We can see the age difference is about 7 years. This is for "pre" and "pre_2" ONLY!
lev_m1_m2[56, c(6,7,9)]
as.numeric(lev_m1_m2[56, 9] - lev_m1_m2[56, 7]) # How much it was off by
```

## Analysis (Part 7.2)
```{r}
# Set up data for "pre" & "pre_3" for AI M2
pre1.3_m2 <- age3_m2 - 2
pre1.3_df <- d[sort(c(pre1.3_m2, age3_m2)),]
pre1_m2 <- which(pre1.3_df$pre_or_post_operation %in% "pre")
pre3_m2 <- which(pre1.3_df$pre_or_post_operation %in% "pre_3")

# Note: Last year's messed up and had c(1,3,5,7,9,11,14,16,18) -> "pre", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "pre_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
pre1_df_m2 <- pre1.3_df[pre1_m2,] 
pre3_df_m2 <- pre1.3_df[pre3_m2,]
```

## Analysis (Part 8.2)
```{r}
pre1.3_diff_m2 <- pre3_df_m2$age_actual - pre1_df_m2$age_actual
pre1_AIage_m2 <- pre1_df_m2$ai_model_2
pre3_AIage_m2 <- pre3_df_m2$ai_model_2
hist(pre1.3_diff_m2)
```

## Analysis (Part 9.2)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time4_age_m2 <- c(which(pre1.3_diff_m2 > 0.5),
                    which(pre1.3_diff_m2 < -0.5))
time4_age_m2 <- sort(time4_age_m2)

time5_age_m2 <- which(pre1.3_diff_m2 >= -1 & 
              pre1.3_diff_m2 <= 1)
time5_age_m2 <- sort(time5_age_m2)

time6_age_m2 <- c(which(pre1.3_diff_m2 < -1),
        which(pre1.3_diff_m2 > 1))
time6_age_m2 <- sort(time6_age_m2)

# Correlations
cor5_m2 <- cor(pre1_AIage_m2, pre3_AIage_m2)
cor6_m2 <- cor(pre1_AIage_m2[time4_age_m2], pre3_AIage_m2[time4_age_m2])
cor7_m2 <- cor(pre1_AIage_m2[time5_age_m2], pre3_AIage_m2[time5_age_m2])
cor8_m2 <- cor(pre1_AIage_m2[time6_age_m2], pre3_AIage_m2[time6_age_m2])

pre1.3_cor_mx_m2 <- data.frame(Correlation=c(cor5_m2, cor6_m2, 
                                             cor7_m2, cor8_m2),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
pre1.3_cor_mx_m2
```

## Analysis (Part 10.2)
```{r}
AIage_m2_m2 <- lm(pre1_AIage_m2 ~ pre3_AIage_m2)
ip_m2_m2 <- influencePlot(AIage_m2_m2)
ip_m2_m2
4/length(pre1_AIage_m2) # Hat-values limit for Influcence Plot
# High Leverage Points: 4 (? > 4/n for Hat-values)
# Outlier Points: 2 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 4 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 11.2)
```{r}
# Finding the Correlation Cofficients for "pre" & "pre_3" for AI M2
pre1.3_cor_old_m2 <- cor(pre1_AIage_m2, pre3_AIage_m2)

pre1.3_cor_compare_m2 <- data.frame(Correlation=c(pre1.3_cor_old_m2),
                             Type=c("All Points"))
pre1.3_cor_compare_m2 # No Bad Leverage Points

# Run the Linear Regression
pre1.3_all_m1_m2 <- lm(pre1_AIage_m2 ~ pre3_AIage_m2)
summary(pre1.3_all_m1_m2)

pre1.3_r_compare_m2 <- data.frame(R_sq=c(summary(pre1.3_all_m1_m2)$r.squared),
                             Type=c("All Points")) 
pre1.3_r_compare_m2 # No Bad Leverage Points
```

## Analysis (Part 12.2)
```{r}
# Set up data for "pre_2" & "pre_3" for AI M2
pre2.3_m2 <- age3_m2 - 1
pre2.3_df <- d[sort(c(pre2.3_m2, age3_m2)),]
pre2_m2 <- which(pre2.3_df$pre_or_post_operation %in% "pre_2")
pre3_m2 <- which(pre2.3_df$pre_or_post_operation %in% "pre_3")

# Note: Last year's messed up and had c(1,3,5,7,10,11,14,16,18) -> "pre_2", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "pre_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
pre2_df_m2 <- pre2.3_df[pre2_m2,] 
pre3_df_m2 <- pre2.3_df[pre3_m2,]
```

## Analysis (Part 13.2)
```{r}
pre2.3_diff_m2 <- pre3_df_m2$age_actual - pre2_df_m2$age_actual
pre2_AIage_m2 <- pre2_df_m2$ai_model_2
pre3_AIage_m2 <- pre3_df_m2$ai_model_2
hist(pre2.3_diff_m2)
```

## Analysis (Part 14.2)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time7_age_m2 <- c(which(pre2.3_diff_m2 > 0.5),
                    which(pre2.3_diff_m2 < -0.5))
time7_age_m2 <- sort(time7_age_m2)

time8_age_m2 <- which(pre2.3_diff_m2 >= -1 & 
              pre2.3_diff_m2 <= 1)
time8_age_m2 <- sort(time8_age_m2)

time9_age_m2 <- c(which(pre2.3_diff_m2 < -1),
        which(pre2.3_diff_m2 > 1))
time9_age_m2 <- sort(time9_age_m2)

# Correlations
cor9_m2 <- cor(pre2_AIage_m2, pre3_AIage_m2)
cor10_m2 <- cor(pre2_AIage_m2[time7_age_m2], pre3_AIage_m2[time7_age_m2])
cor11_m2 <- cor(pre2_AIage_m2[time8_age_m2], pre3_AIage_m2[time8_age_m2])
cor12_m2 <- cor(pre2_AIage_m2[time9_age_m2], pre3_AIage_m2[time9_age_m2])

pre2.3_cor_mx_m2 <- data.frame(Correlation=c(cor9_m2, cor10_m2, 
                                             cor11_m2, cor12_m2),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
pre2.3_cor_mx_m2 # We have N/A since either one or no points for the time given
```

## Analysis (Part 15.2)
```{r}
AIage_m3_m2 <- lm(pre2_AIage_m2 ~ pre3_AIage_m2)
ip_m3_m2 <- influencePlot(AIage_m3_m2)
ip_m3_m2
4/length(pre2_AIage_m2) # Hat-values limit for Influcence Plot
# High Leverage Points: 4 (? > 4/n for Hat-values)
# Outlier Points: 2 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 4 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 16.2)
```{r}
# Finding the Correlation Cofficients for "pre_2" & "pre_3" for AI M2
pre2.3_cor_old_m2 <- cor(pre2_AIage_m2, pre3_AIage_m2)

pre2.3_cor_compare_m2 <- data.frame(Correlation=c(pre2.3_cor_old_m2),
                             Type=c("All Points"))
pre2.3_cor_compare_m2 # No Bad Leverage Points

# Run the Linear Regression
pre2.3_all_m1_m2 <- lm(pre2_AIage_m2 ~ pre3_AIage_m2)
summary(pre2.3_all_m1_m2)

pre2.3_r_compare_m2 <- data.frame(R_sq=c(summary(pre2.3_all_m1_m2)$r.squared),
                             Type=c("All Points")) 
pre2.3_r_compare_m2 # No Bad Leverage Points
```

## Analysis (Part 17.2)
```{r, warning=FALSE, message=FALSE}
every_pre_m2 <- sort(which(d$pre_or_post_operation %in% c("pre", "pre_2",
                                                        "pre_3")))
every_pre_diff_m2 <- d$age_actual[every_pre_m2] - d$ai_model_2[every_pre_m2]
hist(every_pre_diff_m2)
```

## Analysis (Part 18.2)
```{r}
every_pre_actual_m2 <- d$age_actual[every_pre_m2]
every_pre_AIage_m2 <- d$ai_model_2[every_pre_m2]
```

## Analysis (19.2)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time10_age_m2 <- c(which(every_pre_diff_m2 > 0.5),
                    which(every_pre_diff_m2 < -0.5))
time10_age_m2 <- sort(time10_age_m2)

time11_age_m2 <- which(every_pre_diff_m2 >= -1 & 
              every_pre_diff_m2 <= 1)
time11_age_m2 <- sort(time11_age_m2)

time12_age_m2 <- c(which(every_pre_diff_m2 < -1),
        which(every_pre_diff_m2 > 1))
time12_age_m2 <- sort(time12_age_m2)

# Correlations
cor13_m2 <- cor(every_pre_AIage_m2, 
                every_pre_actual_m2)
cor14_m2 <- cor(every_pre_AIage_m2[time10_age_m2],
                every_pre_actual_m2[time10_age_m2])
cor15_m2 <- cor(every_pre_AIage_m2[time11_age_m2],
                every_pre_actual_m2[time11_age_m2])
cor16_m2 <- cor(every_pre_AIage_m2[time12_age_m2],
                every_pre_actual_m2[time12_age_m2])

every_pre_cor_mx_m2 <- data.frame(Correlation=c(cor13_m2, cor14_m2, 
                                             cor15_m2, cor16_m2),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
every_pre_cor_mx_m2
```

## Analysis (Part 20.2)
```{r}
AIage_m4_m2 <- lm(every_pre_AIage_m2 ~ 
                            every_pre_actual_m2)
ip_m4_m2 <- influencePlot(AIage_m4_m2)
ip_m4_m2
4/length(every_pre_actual_m2) # Hat-values limit for Influcence Plot
# High Leverage Points: 35, 137, 165 (? > 4/n for Hat-values)
# Outlier Points: 59, 124, 137 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 35, 165 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: 137 (? > 4/n for Hat values & outside [-2 > ? > +2])
lev_m4_m2 <- d[which(d$pre_or_post_operation %in% c("pre","pre_2","pre_3")),]
lev_m4_m2[137, c(6,7,9)] # (might remove this Bad Leverage)
# We'll see what happens when we remove the Bad Leverage...
```

## Analysis (Part 21.2)
```{r}
# Finding the Correlation Cofficients for ALL "pre-measures" for AI M2
every_pre_cor_old_m2 <- cor(every_pre_AIage_m2, 
                            every_pre_actual_m2)
every_pre_cor_improved_m2 <- cor(every_pre_AIage_m2[-c(137)],
                                 every_pre_actual_m2[-c(137)])

every_pre_cor_compare_m2 <- data.frame(Correlation=c(every_pre_cor_old_m2,
                                                    every_pre_cor_improved_m2),
                             Type=c("All Points", "Removed Bad Leverages"))
every_pre_cor_compare_m2 # Reliability slightly decreased

# Run the Linear Regression
every_all_pre_m1_m2 <- lm(every_pre_AIage_m2 ~
                                 every_pre_actual_m2)
summary(every_all_pre_m1_m2)

every_improved_pre_m1_m2 <- lm(every_pre_AIage_m2[-c(137)] ~
                                 every_pre_actual_m2[-c(137)])
summary(every_improved_pre_m1_m2)

every_all_pre_r_compare_m2 <- data.frame(R_sq=c(summary(every_all_pre_m1_m2)$r.squared,                                        summary(every_improved_pre_m1_m2)$r.squared),
                             Type=c("All Points", "Removed Bad Leverages")) 
every_all_pre_r_compare_m2 # R-squared slightly decreases

# Conclusion: It might be better to not remove the Bad Leverage Point 137 for Model 2. By observation, it approcimately was off by 7 years. This is for comparing ALL "pre-measurements" ONLY!
lev_m4_m2[137, c(7,9)]
as.numeric(lev_m4_m2[137, 9] - lev_m4_m2[137, 7]) # How much it was off by
```



# Testing Reliability for ALL Combinations of "pre-measurements" [AI Model 3]

**NOTE:** The parts are as follows...
  i) "pre" & "pre_2" are Parts 1.3 - 6.3
  ii) "pre" & "pre_3" are Parts 7.3 - 11.3
  iii) "pre_2" & "pre_3" are Parts 12.3 - 16.3
  iv) Every "pre-measurement" are Parts 17.3 - 21.3

## Analysis (Part 1.3)
```{r}
## Re-order the dataset
nrow(d)
for (i in 1:301) {
  if(d$patient_name[i] %in% d$patient_name[i+1])
  {
    if(d$pre_or_post_operation[i] %in% "pre_2" &&
       d$pre_or_post_operation[i+1] %in% "pre")
    {
      temp <- d[i,]
      d[i,] <- d[i+1,]
      d[i+1,] <- temp
    }
  }
}
```

## Analysis (Part 2.3)
```{r, warning=FALSE, message=FALSE}
age11_m3 <- which(d$pre_or_post_operation %in% "pre")
age2_m3 <- which(d$pre_or_post_operation %in% "pre_2")
age3_m3 <- which(d$pre_or_post_operation %in% "pre_3")
all_pre_m3 <- sort(c(age11_m3, age2_m3 ,age3_m3))
age1_m3 <- age2_m3 - 1

age2_pre_m3 <- d$ai_model_3[age2_m3]
age1_pre_m3 <- d$ai_model_3[age1_m3]
age3_pre_m3 <- d$ai_model_3[age3_m3]
pre1.2_diff_m3 <- d$age_actual[age2_m3] - d$age_actual[age1_m3]
hist(pre1.2_diff_m3)
```

## Analysis (Part 3.3)
```{r}
## Compute the coefficient of correlation of two predicted age for "pre" & "pre_2" for AI M3
all_pre1.2_index_m3 <- sort(c(age1_m3, age2_m3))
length(all_pre1.2_index_m3)/2
AIage_pre_m3 <- numeric(57)
AIage_pre2_m3 <- numeric(57)
for (i in 1:57) {
  temp <- i * 2 -1
  if(d$age_actual[all_pre1.2_index_m3[temp]] > 
     d$age_actual[all_pre1.2_index_m3[temp + 1]])
  {
    AIage_pre_m3[i] <- d$ai_model_3[all_pre1.2_index_m3[temp + 1]]
    AIage_pre2_m3[i] <- d$ai_model_3[all_pre1.2_index_m3[temp]]
  }
  else{
    AIage_pre_m3[i] <- d$ai_model_3[all_pre1.2_index_m3[temp]]
    AIage_pre2_m3[i] <- d$ai_model_3[all_pre1.2_index_m3[temp + 1]]
  }
}
```

## Analysis (Part 4.3)
```{r}
pre1.2_age_mx_m3 <- cbind(pre1.2_diff_m3, age2_pre_m3 - age1_pre_m3)
pre1.2_age_mx_m3 # might be better to look at head(...) and tail(...)
# Make subgroups for time
## Over Half Years & Over Full Years
time1_age_m3 <- c(which(pre1.2_diff_m3 > 0.5),
                    which(pre1.2_diff_m3 < -0.5))
time1_age_m3 <- sort(time1_age_m3)

time2_age_m3 <- which(pre1.2_diff_m3 >= -1 & 
              pre1.2_diff_m3 <= 1)
time2_age_m3 <- sort(time2_age_m3)

time3_age_m3 <- c(which(pre1.2_diff_m3 < -1),
        which(pre1.2_diff_m3 > 1))
time3_age_m3 <- sort(time3_age_m3)

# Correlations
cor1_m3 <- cor(AIage_pre_m3, AIage_pre2_m3)
cor2_m3 <- cor(AIage_pre_m3[time1_age_m3], AIage_pre2_m3[time1_age_m3])
cor3_m3 <- cor(AIage_pre_m3[time2_age_m3], AIage_pre2_m3[time2_age_m3])
cor4_m3 <- cor(AIage_pre_m3[time3_age_m3], AIage_pre2_m3[time3_age_m3])

pre1.2_cor_mx_m3 <- data.frame(Correlation=c(cor1_m3, cor2_m3, 
                                             cor3_m3, cor4_m3),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
pre1.2_cor_mx_m3
```

## Analysis (Part 5.3)
```{r}
AIage_m1_m3 <- lm(AIage_pre_m3 ~ AIage_pre2_m3)
ip_m1_m3 <- influencePlot(AIage_m1_m3)
ip_m1_m3
4/length(AIage_pre_m3) # Hat-values limit for Influcence Plot
# High Leverage Points: 40, 56 (? > 4/n for Hat-values)
# Outlier Points: 12, 14, 19 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 40, 56 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 6.3)
```{r}
# Finding the Correlation Cofficients for "pre" & "pre_2" for AI M3
pre1.2_cor_old_m3 <- cor(age1_pre_m3, age2_pre_m3)

pre1.2_cor_compare_m3 <- data.frame(Correlation=c(pre1.2_cor_old_m3),
                             Type=c("All Points"))
pre1.2_cor_compare_m3 # No Bad Leverage Points

# Run the Linear Regression
pre1.2_all_m1_m3 <- lm(age1_pre_m3 ~ age2_pre_m3)
summary(pre1.2_all_m1_m3)

pre1.2_r_compare_m3 <- data.frame(R_sq=c(summary(pre1.2_all_m1_m3)$r.squared),
                             Type=c("All Points")) 
pre1.2_r_compare_m3 # No Bad Leverage Points
```

## Analysis (Part 7.3)
```{r}
# Set up data for "pre" & "pre_3" for AI M3
pre1.3_m3 <- age3_m3 - 2
pre1.3_df <- d[sort(c(pre1.3_m3, age3_m3)),]
pre1_m3 <- which(pre1.3_df$pre_or_post_operation %in% "pre")
pre3_m3 <- which(pre1.3_df$pre_or_post_operation %in% "pre_3")

# Note: Last year's messed up and had c(1,3,5,7,9,11,14,16,18) -> "pre", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "pre_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
pre1_df_m3 <- pre1.3_df[pre1_m3,] 
pre3_df_m3 <- pre1.3_df[pre3_m3,]
```

## Analysis (Part 8.3)
```{r}
pre1.3_diff_m3 <- pre3_df_m3$age_actual - pre1_df_m3$age_actual
pre1_AIage_m3 <- pre1_df_m3$ai_model_3
pre3_AIage_m3 <- pre3_df_m3$ai_model_3
hist(pre1.3_diff_m3)
```

## Analysis (Part 9.3)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time4_age_m3 <- c(which(pre1.3_diff_m3 > 0.5),
                    which(pre1.3_diff_m3 < -0.5))
time4_age_m3 <- sort(time4_age_m3)

time5_age_m3 <- which(pre1.3_diff_m3 >= -1 & 
              pre1.3_diff_m3 <= 1)
time5_age_m3 <- sort(time5_age_m3)

time6_age_m3 <- c(which(pre1.3_diff_m3 < -1),
        which(pre1.3_diff_m3 > 1))
time6_age_m3 <- sort(time6_age_m3)

# Correlations
cor5_m3 <- cor(pre1_AIage_m3, pre3_AIage_m3)
cor6_m3 <- cor(pre1_AIage_m3[time4_age_m3], pre3_AIage_m3[time4_age_m3])
cor7_m3 <- cor(pre1_AIage_m3[time5_age_m3], pre3_AIage_m3[time5_age_m3])
cor8_m3 <- cor(pre1_AIage_m3[time6_age_m3], pre3_AIage_m3[time6_age_m3])

pre1.3_cor_mx_m3 <- data.frame(Correlation=c(cor5_m3, cor6_m3, 
                                             cor7_m3, cor8_m3),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
pre1.3_cor_mx_m3
```

## Analysis (Part 10.3)
```{r}
AIage_m2_m3 <- lm(pre1_AIage_m3 ~ pre3_AIage_m3)
ip_m2_m3 <- influencePlot(AIage_m2_m3)
ip_m2_m3
4/length(pre1_AIage_m3) # Hat-values limit for Influcence Plot
# High Leverage Points: 8 (? > 4/n for Hat-values)
# Outlier Points: 2 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 8 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 11.3)
```{r}
# Finding the Correlation Cofficients for "pre" & "pre_3" for AI M3
pre1.3_cor_old_m3 <- cor(pre1_AIage_m3, pre3_AIage_m3)

pre1.3_cor_compare_m3 <- data.frame(Correlation=c(pre1.3_cor_old_m3),
                             Type=c("All Points"))
pre1.3_cor_compare_m3 # No Bad Leverage Points

# Run the Linear Regression
pre1.3_all_m1_m3 <- lm(pre1_AIage_m3 ~ pre3_AIage_m3)
summary(pre1.3_all_m1_m3)

pre1.3_r_compare_m3 <- data.frame(R_sq=c(summary(pre1.3_all_m1_m3)$r.squared),
                             Type=c("All Points")) 
pre1.3_r_compare_m3 # No Bad Leverage Points
```

## Analysis (Part 12.3)
```{r}
# Set up data for "pre_2" & "pre_3" for AI M3
pre2.3_m3 <- age3_m3 - 1
pre2.3_df <- d[sort(c(pre2.3_m3, age3_m3)),]
pre2_m3 <- which(pre2.3_df$pre_or_post_operation %in% "pre_2")
pre3_m3 <- which(pre2.3_df$pre_or_post_operation %in% "pre_3")

# Note: Last year's messed up and had c(1,3,5,7,10,11,14,16,18) -> "pre_2", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "pre_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
pre2_df_m3 <- pre2.3_df[pre2_m3,] 
pre3_df_m3 <- pre2.3_df[pre3_m3,]
```

## Analysis (Part 13.3)
```{r}
pre2.3_diff_m3 <- pre3_df_m3$age_actual - pre2_df_m3$age_actual
pre2_AIage_m3 <- pre2_df_m3$ai_model_3
pre3_AIage_m3 <- pre3_df_m3$ai_model_3
hist(pre2.3_diff_m3)
```

## Analysis (Part 14.3)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time7_age_m3 <- c(which(pre2.3_diff_m3 > 0.5),
                    which(pre2.3_diff_m3 < -0.5))
time7_age_m3 <- sort(time7_age_m3)

time8_age_m3 <- which(pre2.3_diff_m3 >= -1 & 
              pre2.3_diff_m3 <= 1)
time8_age_m3 <- sort(time8_age_m3)

time9_age_m3 <- c(which(pre2.3_diff_m3 < -1),
        which(pre2.3_diff_m3 > 1))
time9_age_m3 <- sort(time9_age_m3)

# Correlations
cor9_m3 <- cor(pre2_AIage_m3, pre3_AIage_m3)
cor10_m3 <- cor(pre2_AIage_m3[time7_age_m3], pre3_AIage_m3[time7_age_m3])
cor11_m3 <- cor(pre2_AIage_m3[time8_age_m3], pre3_AIage_m3[time8_age_m3])
cor12_m3 <- cor(pre2_AIage_m3[time9_age_m3], pre3_AIage_m3[time9_age_m3])

pre2.3_cor_mx_m3 <- data.frame(Correlation=c(cor9_m3, cor10_m3, 
                                             cor11_m3, cor12_m3),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
pre2.3_cor_mx_m3 # We have N/A since either one or no points for the time given
```

## Analysis (Part 15.3)
```{r}
AIage_m3_m3 <- lm(pre2_AIage_m3 ~ pre3_AIage_m3)
ip_m3_m3 <- influencePlot(AIage_m3_m3)
ip_m3_m3
4/length(pre3_AIage_m3) # Hat-values limit for Influcence Plot
# High Leverage Points: 8 (? > 4/n for Hat-values)
# Outlier Points: 7 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 8 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 16.3)
```{r}
# Finding the Correlation Cofficients for "pre_2" & "pre_3" for AI M3
pre2.3_cor_old_m3 <- cor(pre2_AIage_m3, pre3_AIage_m3)

pre2.3_cor_compare_m3 <- data.frame(Correlation=c(pre2.3_cor_old_m3),
                             Type=c("All Points"))
pre2.3_cor_compare_m3 # No Bad Leverage Points

# Run the Linear Regression
pre2.3_all_m1_m3 <- lm(pre2_AIage_m3 ~ pre3_AIage_m3)
summary(pre2.3_all_m1_m3) # this is a fairly high reliability

pre2.3_r_compare_m3 <- data.frame(R_sq=c(summary(pre2.3_all_m1_m3)$r.squared),
                             Type=c("All Points")) 
pre2.3_r_compare_m3 # No Bad Leverage Points
```

## Analysis (Part 17.3)
```{r, warning=FALSE, message=FALSE}
every_pre_m3 <- sort(which(d$pre_or_post_operation %in% c("pre", "pre_2",
                                                        "pre_3")))
every_pre_diff_m3 <- d$age_actual[every_pre_m3] - d$ai_model_3[every_pre_m3]
hist(every_pre_diff_m3)
```

## Analysis (Part 18.3)
```{r}
every_pre_actual_m3 <- d$age_actual[every_pre_m3]
every_pre_AIage_m3 <- d$ai_model_3[every_pre_m3]
```

## Analysis (19.3)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time10_age_m3 <- c(which(every_pre_diff_m3 > 0.5),
                    which(every_pre_diff_m3 < -0.5))
time10_age_m3 <- sort(time10_age_m3)

time11_age_m3 <- which(every_pre_diff_m3 >= -1 & 
              every_pre_diff_m3 <= 1)
time11_age_m3 <- sort(time11_age_m3)

time12_age_m3 <- c(which(every_pre_diff_m3 < -1),
        which(every_pre_diff_m3 > 1))
time12_age_m3 <- sort(time12_age_m3)

# Correlations
cor13_m3 <- cor(every_pre_AIage_m3, 
                every_pre_actual_m3)
cor14_m3 <- cor(every_pre_AIage_m3[time10_age_m3],
                every_pre_actual_m3[time10_age_m3])
cor15_m3 <- cor(every_pre_AIage_m3[time11_age_m3],
                every_pre_actual_m3[time11_age_m3])
cor16_m3 <- cor(every_pre_AIage_m3[time12_age_m3],
                every_pre_actual_m3[time12_age_m3])

every_pre_cor_mx_m3 <- data.frame(Correlation=c(cor13_m3, cor14_m3, 
                                             cor15_m3, cor16_m3),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
every_pre_cor_mx_m3
```

## Analysis (Part 20.3)
```{r}
AIage_m4_m3 <- lm(every_pre_AIage_m3 ~ 
                            every_pre_actual_m3)
ip_m4_m3 <- influencePlot(AIage_m4_m3)
ip_m4_m3
4/length(every_pre_AIage_m3) # Hat-values limit for Influcence Plot
# High Leverage Points: 35, 165 (? > 4/n for Hat-values)
# Outlier Points: 30, 166 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 35, 165 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 21.3)
```{r}
# Finding the Correlation Cofficients for ALL "pre-measures" for AI M3
every_pre_cor_old_m3 <- cor(every_pre_AIage_m3, 
                            every_pre_actual_m3)

every_pre_cor_compare_m3 <- data.frame(Correlation=c(every_pre_cor_old_m3),
                             Type=c("All Points"))
every_pre_cor_compare_m3 # No Bad Leverage Points

# Run the Linear Regression
every_all_pre_m1_m3 <- lm(every_pre_actual_m3 ~
                                 every_pre_AIage_m3)
summary(every_all_pre_m1_m3)

every_all_pre_r_compare_m3 <- data.frame(R_sq=c(summary(every_all_pre_m1_m3)$r.squared),
                             Type=c("All Points")) 
every_all_pre_r_compare_m3 # No Bad Leverage Points
```



# Pre-Measurements Table
## Model 1
```{r}
pre_table_m1 <- matrix(nrow=4, ncol=5, byrow=TRUE,
                       c(cor1_m1,cor2_m1,cor3_m1,cor4_m1,
                         pre1.2_cor_improved_m1,
                         cor5_m1,cor6_m1,cor7_m1,cor8_m1,
                         NA,
                         cor9_m1,cor10_m1,cor11_m1,cor12_m1,
                         NA,
                         cor13_m1, cor14_m1, cor15_m1, cor16_m1,
                         NA))
rownames(pre_table_m1) <- c("Pre1 - Pre2", "Pre1 - Pre3", "Pre2 - Pre3",
                            "All Pre-Measures")
colnames(pre_table_m1) <- c("No Conditions", "0.5 < Age_Diff < -0.5", 
                                     "1 < Age_Diff < -1", 
                            "-1 < Age_Diff < 1", "Removed Bad Leverage(s)")

# c("No Conditions", "Over Half Year", "Over Full Year", "Within 1 Year", "Removed Bad Leverage(s)) -> translation for what the conditions mean above
pre_table_m1
```

## Model 2
```{r}
pre_table_m2 <- matrix(nrow=4, ncol=5, byrow=TRUE,
                       c(cor1_m2,cor2_m2,cor3_m2,cor4_m2,
                         pre1.2_cor_improved_m2,
                         cor5_m2,cor6_m2,cor7_m2,cor8_m2,
                         NA,
                         cor9_m2,cor10_m2,cor11_m2,cor12_m2,
                         NA,
                         cor13_m2, cor14_m2, cor15_m2, cor16_m2,
                         every_pre_cor_improved_m2))
rownames(pre_table_m2) <- c("Pre1 - Pre2", "Pre1 - Pre3", "Pre2 - Pre3",
                            "All Pre-Measures")
colnames(pre_table_m2) <- c("No Conditions", "0.5 < Age_Diff < -0.5", 
                                     "1 < Age_Diff < -1", 
                            "-1 < Age_Diff < 1", "Removed Bad Leverage(s)")

# c("No Conditions", "Over Half Year", "Over Full Year", "Within 1 Year", "Removed Bad Leverage(s)) -> translation for what the conditions mean above
pre_table_m2
```

## Model 3
```{r}
pre_table_m3 <- matrix(nrow=4, ncol=5, byrow=TRUE,
                       c(cor1_m3,cor2_m3,cor3_m3,cor4_m3,
                         NA,
                         cor5_m3,cor6_m3,cor7_m3,cor8_m3,
                         NA,
                         cor9_m3,cor10_m3,cor11_m3,cor12_m3,
                         NA,
                         cor13_m3, cor14_m3, cor15_m3, cor16_m3,
                         NA))
rownames(pre_table_m3) <- c("Pre1 - Pre2", "Pre1 - Pre3", "Pre2 - Pre3",
                            "All Pre-Measures")
colnames(pre_table_m3) <- c("No Conditions", "0.5 < Age_Diff < -0.5", 
                                     "1 < Age_Diff < -1", 
                            "-1 < Age_Diff < 1", "Removed Bad Leverage(s)")

# c("No Conditions", "Over Half Year", "Over Full Year", "Within 1 Year", "Removed Bad Leverage(s)) -> translation for what the conditions mean above
pre_table_m3

# Interestingly enough, for all of Model 3's "Pre-Measures" and its combinations, it did not have any point where it had Bad Leverage Points.
```



# Accuracy for Each "Pre-Measures"
## Set up for showing the comparisons for each Models
```{r}
# Model 1
pre1.2_MSE_m1 <- mean((pre1.2_all_m1_m1$residuals)^2)
pre1.3_MSE_m1 <- mean((pre1.3_all_m1_m1$residuals)^2)
pre2.3_MSE_m1 <- mean((pre2.3_all_m1_m1$residuals)^2)
pre_every_MSE_m1 <- mean((every_all_pre_m1_m1$residuals)^2)
pre1.2_improved_MSE_m1 <- mean((pre1.2_improved_m1_m1$residuals)^2)


# Model 2
pre1.2_MSE_m2 <- mean((pre1.2_all_m1_m2$residuals)^2)
pre1.3_MSE_m2 <- mean((pre1.3_all_m1_m2$residuals)^2)
pre2.3_MSE_m2 <- mean((pre2.3_all_m1_m2$residuals)^2)
pre_every_MSE_m2 <- mean((every_all_pre_m1_m2$residuals)^2)
pre1.2_improved_MSE_m2 <- mean((pre1.2_improved_m1_m2$residuals)^2)
pre_every_improved_MSE_m2 <- mean((every_improved_pre_m1_m2$residuals)^2)


# Model 3
pre1.2_MSE_m3 <- mean((pre1.2_all_m1_m3$residuals)^2)
pre1.3_MSE_m3 <- mean((pre1.3_all_m1_m3$residuals)^2)
pre2.3_MSE_m3 <- mean((pre2.3_all_m1_m3$residuals)^2)
pre_every_MSE_m3 <- mean((every_all_pre_m1_m3$residuals)^2)


# Show the differences amongst the Models for MSE (Numerically)
pre_MSE_m1 <- data.frame(Combination=c("Pre - Pre2", "Pre - Pre3",
                                       "Pre2 - Pre3", "All Pre-Measures",
                                       "Removed Bad Leverage(s): Pre - Pre2"),
                         MSE=c(pre1.2_MSE_m1, pre1.3_MSE_m1,
                               pre2.3_MSE_m1, pre_every_MSE_m1,
                               pre1.2_improved_MSE_m1))

pre_MSE_m2 <- data.frame(Combination=c("Pre - Pre2", "Pre - Pre3",
                                       "Pre2 - Pre3", "All Pre-Measures",
                                       "Removed Bad Leverage(s): Pre - Pre2",
                                       "Removed Bad Leverage(s): All Pre"),
                         MSE=c(pre1.2_MSE_m2, pre1.3_MSE_m2,
                               pre2.3_MSE_m2, pre_every_MSE_m2,
                               pre1.2_improved_MSE_m2,
                               pre_every_improved_MSE_m2))

pre_MSE_m3 <- data.frame(Combination=c("Pre - Pre2", "Pre - Pre3",
                                       "Pre2 - Pre3", "All Pre-Measures"),
                         MSE=c(pre1.2_MSE_m3, pre1.3_MSE_m3,
                               pre2.3_MSE_m3, pre_every_MSE_m3))


pre_MSE_all <- data.frame(Combination=c("Pre - Pre2", "Pre - Pre3",
                                       "Pre2 - Pre3", "All Pre-Measures",
                                       "Removed Bad Leverage(s): Pre - Pre2",
                                       "Removed Bad Leverage(s): All Pre"),
                          `MSE Model 1`=c(pre1.2_MSE_m1, pre1.3_MSE_m1,
                               pre2.3_MSE_m1, pre_every_MSE_m1,
                               pre1.2_improved_MSE_m1, NA),
                         `MSE Model 2`=c(pre1.2_MSE_m2, pre1.3_MSE_m2,
                               pre2.3_MSE_m2, pre_every_MSE_m2,
                               pre1.2_improved_MSE_m2,
                               pre_every_improved_MSE_m2),
                         `MSE Model 3`=c(pre1.2_MSE_m3, pre1.3_MSE_m3,
                               pre2.3_MSE_m3, pre_every_MSE_m3, NA, NA))

```

## Show the comparisons for each Models (Numerical)
```{r}
pre_MSE_m1
pre_MSE_m2
pre_MSE_m3
pre_MSE_all
```




# Testing Reliability for ALL Combinations of "post-measurements" [AI Model 1]

**NOTE:** The parts are as follows...
  i) "post" & "post_2" are Parts 1.1 - 6.1
  ii) "post" & "post_3" are Parts 7.1 - 11.1
  iii) "post_2" & "post_3" are Parts 12.1 - 16.1
  iv) Every "post-measurement" are Parts 17.1 - 21.1

## Analysis (Part 1.1)
```{r}
## Re-order the dataset
nrow(d)
for (i in 1:301) {
  if(d$patient_name[i] %in% d$patient_name[i+1])
  {
    if(d$pre_or_post_operation[i] %in% "post_2" &&
       d$pre_or_post_operation[i+1] %in% "post")
    {
      temp <- d[i,]
      d[i,] <- d[i+1,]
      d[i+1,] <- temp
    }
  }
}
```

## Analysis (Part 2.1)
```{r, warning=FALSE, message=FALSE}
age11_m1 <- which(d$pre_or_post_operation %in% "post")
age2_m1 <- which(d$pre_or_post_operation %in% "post_2")
age3_m1 <- which(d$pre_or_post_operation %in% "post_3")
all_post_m1 <- sort(c(age11_m1, age2_m1 ,age3_m1))
age1_m1 <- age2_m1 - 1

age2_post_m1 <- d$ai_model_1[age2_m1]
age1_post_m1 <- d$ai_model_1[age1_m1]
age3_post_m1 <- d$ai_model_1[age3_m1]
post1.2_diff_m1 <- d$age_actual[age2_m1] - d$age_actual[age1_m1]
hist(post1.2_diff_m1)
```

## Analysis (Part 3.1)
```{r}
## Compute the coefficient of correlation of two postdicted age for "post" & "post_2" for AI M1
all_post1.2_index_m1 <- sort(c(age1_m1, age2_m1))
length(all_post1.2_index_m1)/2
AIage_post_m1 <- numeric(24)
AIage_post2_m1 <- numeric(24)
for (i in 1:24) {
  temp <- i * 2 -1
  if(d$age_actual[all_post1.2_index_m1[temp]] > 
     d$age_actual[all_post1.2_index_m1[temp + 1]])
  {
    AIage_post_m1[i] <- d$ai_model_1[all_post1.2_index_m1[temp + 1]]
    AIage_post2_m1[i] <- d$ai_model_1[all_post1.2_index_m1[temp]]
  }
  else{
    AIage_post_m1[i] <- d$ai_model_1[all_post1.2_index_m1[temp]]
    AIage_post2_m1[i] <- d$ai_model_1[all_post1.2_index_m1[temp + 1]]
  }
}
```

## Analysis (Part 4.1)
```{r}
post1.2_age_mx_m1 <- cbind(post1.2_diff_m1, age2_post_m1 - age1_post_m1)
post1.2_age_mx_m1 # might be better to look at head(...) and tail(...)
# Make subgroups for time
## Over Half Years & Over Full Years
time1_age_m1 <- c(which(post1.2_diff_m1 > 0.5),
                    which(post1.2_diff_m1 < -0.5))
time1_age_m1 <- sort(time1_age_m1)

time2_age_m1 <- which(post1.2_diff_m1 >= -1 & 
              post1.2_diff_m1 <= 1)
time2_age_m1 <- sort(time2_age_m1)

time3_age_m1 <- c(which(post1.2_diff_m1 < -1),
        which(post1.2_diff_m1 > 1))
time3_age_m1 <- sort(time3_age_m1)

# Correlations
cor1_m1 <- cor(AIage_post_m1, AIage_post2_m1)
cor2_m1 <- cor(AIage_post_m1[time1_age_m1], AIage_post2_m1[time1_age_m1])
cor3_m1 <- cor(AIage_post_m1[time2_age_m1], AIage_post2_m1[time2_age_m1])
cor4_m1 <- cor(AIage_post_m1[time3_age_m1], AIage_post2_m1[time3_age_m1])

post1.2_cor_mx_m1 <- data.frame(Correlation=c(cor1_m1, cor2_m1, 
                                             cor3_m1, cor4_m1),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
post1.2_cor_mx_m1
```

## Analysis (Part 5.1)
```{r}
AIage_m1_m1 <- lm(AIage_post_m1 ~ AIage_post2_m1)
ip_m1_m1 <- influencePlot(AIage_m1_m1)
ip_m1_m1
4/length(AIage_post_m1) # Hat-values limit for Influcence Plot
# High Leverage Points: 7, 24 (? > 4/n for Hat-values)
# Outlier Points: 9, 10, 11 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 7, 24 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 6.1)
```{r}
# Finding the Correlation Cofficients for "post" & "post_2" for AI M1
post1.2_cor_old_m1 <- cor(age1_post_m1, age2_post_m1)

post1.2_cor_compare_m1 <- data.frame(Correlation=c(post1.2_cor_old_m1),
                             Type=c("All Points"))
post1.2_cor_compare_m1 # No Bad Leverage Points

# Run the Linear Regression
post1.2_all_m1_m1 <- lm(age1_post_m1 ~ age2_post_m1)
summary(post1.2_all_m1_m1)

post1.2_r_compare_m1 <- data.frame(R_sq=c(summary(post1.2_all_m1_m1)$r.squared),
                             Type=c("All Points")) 
post1.2_r_compare_m1 # No Bad Leverage Points
```

## Analysis (Part 7.1)
```{r}
# Set up data for "post" & "post_3" for AI M1
post1.3_m1 <- age3_m1 - 2
post1.3_df <- d[sort(c(post1.3_m1, age3_m1)),]
post1_m1 <- which(post1.3_df$pre_or_post_operation %in% "post")
post3_m1 <- which(post1.3_df$pre_or_post_operation %in% "post_3")

# Note: Last year's messed up and had c(1,3,5,7,9,11,14,16,18) -> "post", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "post_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
post1_df_m1 <- post1.3_df[post1_m1,]
post3_df_m1 <- post1.3_df[post3_m1,]
```

## Analysis (Part 8.1)
```{r}
post1.3_diff_m1 <- post3_df_m1$age_actual - post1_df_m1$age_actual
post1_AIage_m1 <- post1_df_m1$ai_model_1
post3_AIage_m1 <- post3_df_m1$ai_model_1
hist(post1.3_diff_m1)
```

## Analysis (Part 9.1)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time4_age_m1 <- c(which(post1.3_diff_m1 > 0.5),
                    which(post1.3_diff_m1 < -0.5))
time4_age_m1 <- sort(time4_age_m1)

time5_age_m1 <- which(post1.3_diff_m1 >= -1 & 
              post1.3_diff_m1 <= 1)
time5_age_m1 <- sort(time5_age_m1)

time6_age_m1 <- c(which(post1.3_diff_m1 < -1),
        which(post1.3_diff_m1 > 1))
time6_age_m1 <- sort(time6_age_m1)

# Correlations
cor5_m1 <- cor(post1_AIage_m1, post3_AIage_m1)
cor6_m1 <- cor(post1_AIage_m1[time4_age_m1], post3_AIage_m1[time4_age_m1])
cor7_m1 <- cor(post1_AIage_m1[time5_age_m1], post3_AIage_m1[time5_age_m1])
cor8_m1 <- cor(post1_AIage_m1[time6_age_m1], post3_AIage_m1[time6_age_m1])

post1.3_cor_mx_m1 <- data.frame(Correlation=c(cor5_m1, cor6_m1, 
                                             cor7_m1, cor8_m1),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
post1.3_cor_mx_m1
```

## Analysis (Part 10.1)
```{r}
AIage_m2_m1 <- lm(post1_AIage_m1 ~ post3_AIage_m1)
ip_m2_m1 <- influencePlot(AIage_m2_m1)
ip_m2_m1
4/length(post3_AIage_m1) # Hat-values limit for Influcence Plot
# High Leverage Points: N/A (? > 4/n for Hat-values)
# Outlier Points: 5 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: N/A (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 11.1)
```{r}
# Finding the Correlation Cofficients for "post" & "post_3" for AI M1
post1.3_cor_old_m1 <- cor(post1_AIage_m1, post3_AIage_m1)

post1.3_cor_compare_m1 <- data.frame(Correlation=c(post1.3_cor_old_m1),
                             Type=c("All Points"))
post1.3_cor_compare_m1 # No Bad Leverage Points

# Run the Linear Regression
post1.3_all_m1_m1 <- lm(post1_AIage_m1 ~ post3_AIage_m1)
summary(post1.3_all_m1_m1)

post1.3_r_compare_m1 <- data.frame(R_sq=c(summary(post1.3_all_m1_m1)$r.squared),
                             Type=c("All Points")) 
post1.3_r_compare_m1 # No Bad Leverage Points
```

## Analysis (Part 12.1)
```{r}
# Set up data for "post_2" & "post_3" for AI M1
post2.3_m1 <- age3_m1 - 1
post2.3_df <- d[sort(c(post2.3_m1, age3_m1)),]
post2_m1 <- which(post2.3_df$pre_or_post_operation %in% "post_2")
post3_m1 <- which(post2.3_df$pre_or_post_operation %in% "post_3")

# Note: Last year's messed up and had c(1,3,5,7,10,11,14,16,18) -> "post_2", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "post_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
post2_df_m1 <- post2.3_df[post2_m1,] 
post3_df_m1 <- post2.3_df[post3_m1,]
```

## Analysis (Part 13.1)
```{r}
post2.3_diff_m1 <- post3_df_m1$age_actual - post2_df_m1$age_actual
post2_AIage_m1 <- post2_df_m1$ai_model_1
post3_AIage_m1 <- post3_df_m1$ai_model_1
hist(post2.3_diff_m1)
```

## Analysis (Part 14.1)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time7_age_m1 <- c(which(post2.3_diff_m1 > 0.5),
                    which(post2.3_diff_m1 < -0.5))
time7_age_m1 <- sort(time7_age_m1)

time8_age_m1 <- which(post2.3_diff_m1 >= -1 & 
              post2.3_diff_m1 <= 1)
time8_age_m1 <- sort(time8_age_m1)

time9_age_m1 <- c(which(post2.3_diff_m1 < -1),
        which(post2.3_diff_m1 > 1))
time9_age_m1 <- sort(time9_age_m1)

# Correlations
cor9_m1 <- cor(post2_AIage_m1, post3_AIage_m1)
cor10_m1 <- cor(post2_AIage_m1[time7_age_m1], post3_AIage_m1[time7_age_m1])
cor11_m1 <- cor(post2_AIage_m1[time8_age_m1], post3_AIage_m1[time8_age_m1])
cor12_m1 <- cor(post2_AIage_m1[time9_age_m1], post3_AIage_m1[time9_age_m1])

post2.3_cor_mx_m1 <- data.frame(Correlation=c(cor9_m1, cor10_m1, 
                                             cor11_m1, cor12_m1),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
post2.3_cor_mx_m1 # We have N/A since either one or no points for the time given
```

## Analysis (Part 15.1)
```{r}
AIage_m3_m1 <- lm(post2_AIage_m1 ~ post3_AIage_m1)
ip_m3_m1 <- influencePlot(AIage_m3_m1)
ip_m3_m1
4/length(post2_AIage_m1) # Hat-values limit for Influcence Plot
# High Leverage Points: N/A (? > 4/n for Hat-values)
# Outlier Points: N/A (StudRes is either [-2 > ? > +2])
# Good Leverage Points: N/A (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 16.1)
```{r}
# Finding the Correlation Cofficients for "post_2" & "post_3" for AI M1
post2.3_cor_old_m1 <- cor(post2_AIage_m1, post3_AIage_m1)

post2.3_cor_compare_m1 <- data.frame(Correlation=c(post2.3_cor_old_m1),
                             Type=c("All Points"))
post2.3_cor_compare_m1 # No Bag Leverage Points

# Run the Linear Regression
post2.3_all_m1_m1 <- lm(post2_AIage_m1 ~ post3_AIage_m1)
summary(post2.3_all_m1_m1)

post2.3_r_compare_m1 <- data.frame(R_sq=c(summary(post2.3_all_m1_m1)$r.squared),
                             Type=c("All Points")) 
post2.3_r_compare_m1 # No Bad Leverage Points
```

## Analysis (Part 17.1)
```{r, warning=FALSE, message=FALSE}
every_post_m1 <- sort(which(d$pre_or_post_operation %in% c("post", "post_2",
                                                        "post_3")))
every_post_diff_m1 <- d$age_actual[every_post_m1] - d$ai_model_1[every_post_m1]
hist(every_post_diff_m1)
```

## Analysis (Part 18.1)
```{r}
every_post_actual_m1 <- d$age_actual[every_post_m1]
every_post_AIage_m1 <- d$ai_model_1[every_post_m1]
```

## Analysis (19.1)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time10_age_m1 <- c(which(every_post_diff_m1 > 0.5),
                    which(every_post_diff_m1 < -0.5))
time10_age_m1 <- sort(time10_age_m1)

time11_age_m1 <- which(every_post_diff_m1 >= -1 & 
              every_post_diff_m1 <= 1)
time11_age_m1 <- sort(time11_age_m1)

time12_age_m1 <- c(which(every_post_diff_m1 < -1),
        which(every_post_diff_m1 > 1))
time12_age_m1 <- sort(time12_age_m1)

# Correlations
cor13_m1 <- cor(every_post_AIage_m1, 
                every_post_actual_m1)
cor14_m1 <- cor(every_post_AIage_m1[time10_age_m1],
                every_post_actual_m1[time10_age_m1])
cor15_m1 <- cor(every_post_AIage_m1[time11_age_m1],
                every_post_actual_m1[time11_age_m1])
cor16_m1 <- cor(every_post_AIage_m1[time12_age_m1],
                every_post_actual_m1[time12_age_m1])

every_post_cor_mx_m1 <- data.frame(Correlation=c(cor13_m1, cor14_m1, 
                                             cor15_m1, cor16_m1),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
every_post_cor_mx_m1
```

## Analysis (Part 20.1)
```{r}
AIage_m4_m1 <- lm(every_post_AIage_m1 ~ 
                            every_post_actual_m1)
ip_m4_m1 <- influencePlot(AIage_m4_m1)
ip_m4_m1
4/length(every_post_actual_m1) # Hat-values limit for Influcence Plot
# High Leverage Points: 18, 27, 28 (? > 4/n for Hat-values)
# Outlier Points: 11, 130 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 18, 27, 28 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2]
```

## Analysis (Part 21.1)
```{r}
# Finding the Correlation Cofficients for ALL "post-measures" for AI M1
every_post_cor_old_m1 <- cor(every_post_AIage_m1, 
                            every_post_actual_m1)

every_post_cor_compare_m1 <- data.frame(Correlation=c(every_post_cor_old_m1),
                             Type=c("All Points"))
every_post_cor_compare_m1 # No Bad Leverage Points

# Run the Linear Regression
every_all_post_m1_m1 <- lm(every_post_AIage_m1 ~
                                 every_post_actual_m1)
summary(every_all_post_m1_m1)

every_all_post_r_compare_m1 <- data.frame(R_sq=c(summary(every_all_post_m1_m1)$r.squared),
                             Type=c("All Points")) 
every_all_post_r_compare_m1 # No Bad Leverage Points
```



# Testing Reliability for ALL Combinations of "post-measurements" [AI Model 2]

**NOTE:** The parts are as follows...
  i) "post" & "post_2" are Parts 1.2 - 6.2
  ii) "post" & "post_3" are Parts 7.2 - 11.2
  iii) "post_2" & "post_3" are Parts 12.2 - 16.2
  iv) Every "post-measurement" are Parts 17.2 - 21.2

## Analysis (Part 1.2)
```{r}
## Re-order the dataset
nrow(d)
for (i in 1:301) {
  if(d$patient_name[i] %in% d$patient_name[i+1])
  {
    if(d$pre_or_post_operation[i] %in% "post_2" &&
       d$pre_or_post_operation[i+1] %in% "post")
    {
      temp <- d[i,]
      d[i,] <- d[i+1,]
      d[i+1,] <- temp
    }
  }
}
```

## Analysis (Part 2.2)
```{r, warning=FALSE, message=FALSE}
age11_m2 <- which(d$pre_or_post_operation %in% "post")
age2_m2 <- which(d$pre_or_post_operation %in% "post_2")
age3_m2 <- which(d$pre_or_post_operation %in% "post_3")
all_post_m2 <- sort(c(age11_m2, age2_m2 ,age3_m2))
age1_m2 <- age2_m2 - 1

age2_post_m2 <- d$ai_model_2[age2_m2]
age1_post_m2 <- d$ai_model_2[age1_m2]
age3_post_m2 <- d$ai_model_2[age3_m2]
post1.2_diff_m2 <- d$age_actual[age2_m2] - d$age_actual[age1_m2]
hist(post1.2_diff_m2)
```

## Analysis (Part 3.2)
```{r}
## Compute the coefficient of correlation of two postdicted age for "post" & "post_2" for AI M2
all_post1.2_index_m2 <- sort(c(age1_m2, age2_m2))
length(all_post1.2_index_m2)/2
AIage_post_m2 <- numeric(24)
AIage_post2_m2 <- numeric(24)
for (i in 1:24) {
  temp <- i * 2 -1
  if(d$age_actual[all_post1.2_index_m2[temp]] > 
     d$age_actual[all_post1.2_index_m2[temp + 1]])
  {
    AIage_post_m2[i] <- d$ai_model_2[all_post1.2_index_m2[temp + 1]]
    AIage_post2_m2[i] <- d$ai_model_2[all_post1.2_index_m2[temp]]
  }
  else{
    AIage_post_m2[i] <- d$ai_model_2[all_post1.2_index_m2[temp]]
    AIage_post2_m2[i] <- d$ai_model_2[all_post1.2_index_m2[temp + 1]]
  }
}
```

## Analysis (Part 4.2)
```{r}
post1.2_age_mx_m2 <- cbind(post1.2_diff_m2, age2_post_m2 - age1_post_m2)
post1.2_age_mx_m2 # might be better to look at head(...) and tail(...)
# Make subgroups for time
## Over Half Years & Over Full Years
time1_age_m2 <- c(which(post1.2_diff_m2 > 0.5),
                    which(post1.2_diff_m2 < -0.5))
time1_age_m2 <- sort(time1_age_m2)

time2_age_m2 <- which(post1.2_diff_m2 >= -1 & 
              post1.2_diff_m2 <= 1)
time2_age_m2 <- sort(time2_age_m2)

time3_age_m2 <- c(which(post1.2_diff_m2 < -1),
        which(post1.2_diff_m2 > 1))
time3_age_m2 <- sort(time3_age_m2)

# Correlations
cor1_m2 <- cor(AIage_post_m2, AIage_post2_m2)
cor2_m2 <- cor(AIage_post_m2[time1_age_m2], AIage_post2_m2[time1_age_m2])
cor3_m2 <- cor(AIage_post_m2[time2_age_m2], AIage_post2_m2[time2_age_m2])
cor4_m2 <- cor(AIage_post_m2[time3_age_m2], AIage_post2_m2[time3_age_m2])

post1.2_cor_mx_m2 <- data.frame(Correlation=c(cor1_m2, cor2_m2, 
                                             cor3_m2, cor4_m2),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
post1.2_cor_mx_m2
```

## Analysis (Part 5.2)
```{r}
AIage_m1_m2 <- lm(AIage_post_m2 ~ AIage_post2_m2)
ip_m1_m2 <- influencePlot(AIage_m1_m2)
ip_m1_m2
4/length(AIage_post_m2) # Hat-values limit for Influcence Plot
# High Leverage Points: 18 (? > 4/n for Hat-values)
# Outlier Points: 2, 10 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 18 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 6.2)
```{r}
# Finding the Correlation Cofficients for "post" & "post_2" for AI M2
post1.2_cor_old_m2 <- cor(age1_post_m2, age2_post_m2)

post1.2_cor_compare_m2 <- data.frame(Correlation=c(post1.2_cor_old_m2),
                             Type=c("All Points"))
post1.2_cor_compare_m2 # No Bad Leverage Points

# Run the Linear Regression
post1.2_all_m1_m2 <- lm(age1_post_m2 ~ age2_post_m2)
summary(post1.2_all_m1_m2)

post1.2_r_compare_m2 <- data.frame(R_sq=c(summary(post1.2_all_m1_m2)$r.squared),
                             Type=c("All Points")) 
post1.2_r_compare_m2 # No Bad Leverage Points
```

## Analysis (Part 7.2)
```{r}
# Set up data for "post" & "post_3" for AI M2
post1.3_m2 <- age3_m2 - 2
post1.3_df <- d[sort(c(post1.3_m2, age3_m2)),]
post1_m2 <- which(post1.3_df$pre_or_post_operation %in% "post")
post3_m2 <- which(post1.3_df$pre_or_post_operation %in% "post_3")

# Note: Last year's messed up and had c(1,3,5,7,9,11,14,16,18) -> "post", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "post_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
post1_df_m2 <- post1.3_df[post1_m2,] 
post3_df_m2 <- post1.3_df[post3_m2,]
```

## Analysis (Part 8.2)
```{r}
post1.3_diff_m2 <- post3_df_m2$age_actual - post1_df_m2$age_actual
post1_AIage_m2 <- post1_df_m2$ai_model_2
post3_AIage_m2 <- post3_df_m2$ai_model_2
hist(post1.3_diff_m2)
```

## Analysis (Part 9.2)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time4_age_m2 <- c(which(post1.3_diff_m2 > 0.5),
                    which(post1.3_diff_m2 < -0.5))
time4_age_m2 <- sort(time4_age_m2)

time5_age_m2 <- which(post1.3_diff_m2 >= -1 & 
              post1.3_diff_m2 <= 1)
time5_age_m2 <- sort(time5_age_m2)

time6_age_m2 <- c(which(post1.3_diff_m2 < -1),
        which(post1.3_diff_m2 > 1))
time6_age_m2 <- sort(time6_age_m2)

# Correlations
cor5_m2 <- cor(post1_AIage_m2, post3_AIage_m2)
cor6_m2 <- cor(post1_AIage_m2[time4_age_m2], post3_AIage_m2[time4_age_m2])
cor7_m2 <- cor(post1_AIage_m2[time5_age_m2], post3_AIage_m2[time5_age_m2])
cor8_m2 <- cor(post1_AIage_m2[time6_age_m2], post3_AIage_m2[time6_age_m2])

post1.3_cor_mx_m2 <- data.frame(Correlation=c(cor5_m2, cor6_m2, 
                                             cor7_m2, cor8_m2),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
post1.3_cor_mx_m2
```

## Analysis (Part 10.2)
```{r}
AIage_m2_m2 <- lm(post1_AIage_m2 ~ post3_AIage_m2)
ip_m2_m2 <- influencePlot(AIage_m2_m2)
ip_m2_m2
4/length(post1_AIage_m2) # Hat-values limit for Influcence Plot
# High Leverage Points: N/A (? > 4/n for Hat-values)
# Outlier Points: N/A (StudRes is either [-2 > ? > +2])
# Good Leverage Points: N/A (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 11.2)
```{r}
# Finding the Correlation Cofficients for "post" & "post_3" for AI M2
post1.3_cor_old_m2 <- cor(post1_AIage_m2, post3_AIage_m2)

post1.3_cor_compare_m2 <- data.frame(Correlation=c(post1.3_cor_old_m2),
                             Type=c("All Points"))
post1.3_cor_compare_m2 # No Bad Leverage Points

# Run the Linear Regression
post1.3_all_m1_m2 <- lm(post1_AIage_m2 ~ post3_AIage_m2)
summary(post1.3_all_m1_m2)

post1.3_r_compare_m2 <- data.frame(R_sq=c(summary(post1.3_all_m1_m2)$r.squared),
                             Type=c("All Points")) 
post1.3_r_compare_m2 # No Bad Leverage Points
```

## Analysis (Part 12.2)
```{r}
# Set up data for "post_2" & "post_3" for AI M2
post2.3_m2 <- age3_m2 - 1
post2.3_df <- d[sort(c(post2.3_m2, age3_m2)),]
post2_m2 <- which(post2.3_df$pre_or_post_operation %in% "post_2")
post3_m2 <- which(post2.3_df$pre_or_post_operation %in% "post_3")

# Note: Last year's messed up and had c(1,3,5,7,10,11,14,16,18) -> "post_2", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "post_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
post2_df_m2 <- post2.3_df[post2_m2,] 
post3_df_m2 <- post2.3_df[post3_m2,]
```

## Analysis (Part 13.2)
```{r}
post2.3_diff_m2 <- post3_df_m2$age_actual - post2_df_m2$age_actual
post2_AIage_m2 <- post2_df_m2$ai_model_2
post3_AIage_m2 <- post3_df_m2$ai_model_2
hist(post2.3_diff_m2)
```

## Analysis (Part 14.2)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time7_age_m2 <- c(which(post2.3_diff_m2 > 0.5),
                    which(post2.3_diff_m2 < -0.5))
time7_age_m2 <- sort(time7_age_m2)

time8_age_m2 <- which(post2.3_diff_m2 >= -1 & 
              post2.3_diff_m2 <= 1)
time8_age_m2 <- sort(time8_age_m2)

time9_age_m2 <- c(which(post2.3_diff_m2 < -1),
        which(post2.3_diff_m2 > 1))
time9_age_m2 <- sort(time9_age_m2)

# Correlations
cor9_m2 <- cor(post2_AIage_m2, post3_AIage_m2)
cor10_m2 <- cor(post2_AIage_m2[time7_age_m2], post3_AIage_m2[time7_age_m2])
cor11_m2 <- cor(post2_AIage_m2[time8_age_m2], post3_AIage_m2[time8_age_m2])
cor12_m2 <- cor(post2_AIage_m2[time9_age_m2], post3_AIage_m2[time9_age_m2])

post2.3_cor_mx_m2 <- data.frame(Correlation=c(cor9_m2, cor10_m2, 
                                             cor11_m2, cor12_m2),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
post2.3_cor_mx_m2 # We have N/A since either one or no points for the time given
```

## Analysis (Part 15.2)
```{r}
AIage_m3_m2 <- lm(post2_AIage_m2 ~ post3_AIage_m2)
ip_m3_m2 <- influencePlot(AIage_m3_m2)
ip_m3_m2
4/length(post2_AIage_m2) # Hat-values limit for Influcence Plot
# High Leverage Points: 4 (? > 4/n for Hat-values)
# Outlier Points: N/A (StudRes is either [-2 > ? > +2])
# Good Leverage Points: N/A (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 16.2)
```{r}
# Finding the Correlation Cofficients for "post_2" & "post_3" for AI M2
post2.3_cor_old_m2 <- cor(post2_AIage_m2, post3_AIage_m2)

post2.3_cor_compare_m2 <- data.frame(Correlation=c(post2.3_cor_old_m2),
                             Type=c("All Points"))
post2.3_cor_compare_m2 # No Bad Leverage Points

# Run the Linear Regression
post2.3_all_m1_m2 <- lm(post2_AIage_m2 ~ post3_AIage_m2)
summary(post2.3_all_m1_m2)

post2.3_r_compare_m2 <- data.frame(R_sq=c(summary(post2.3_all_m1_m2)$r.squared),
                             Type=c("All Points")) 
post2.3_r_compare_m2 # No Bad Leverage Points
```

## Analysis (Part 17.2)
```{r, warning=FALSE, message=FALSE}
every_post_m2 <- sort(which(d$pre_or_post_operation %in% c("post", "post_2",
                                                        "post_3")))
every_post_diff_m2 <- d$age_actual[every_post_m2] - d$ai_model_2[every_post_m2]
hist(every_post_diff_m2)
```

## Analysis (Part 18.2)
```{r}
every_post_actual_m2 <- d$age_actual[every_post_m2]
every_post_AIage_m2 <- d$ai_model_2[every_post_m2]
```

## Analysis (19.2)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time10_age_m2 <- c(which(every_post_diff_m2 > 0.5),
                    which(every_post_diff_m2 < -0.5))
time10_age_m2 <- sort(time10_age_m2)

time11_age_m2 <- which(every_post_diff_m2 >= -1 & 
              every_post_diff_m2 <= 1)
time11_age_m2 <- sort(time11_age_m2)

time12_age_m2 <- c(which(every_post_diff_m2 < -1),
        which(every_post_diff_m2 > 1))
time12_age_m2 <- sort(time12_age_m2)

# Correlations
cor13_m2 <- cor(every_post_AIage_m2, 
                every_post_actual_m2)
cor14_m2 <- cor(every_post_AIage_m2[time10_age_m2],
                every_post_actual_m2[time10_age_m2])
cor15_m2 <- cor(every_post_AIage_m2[time11_age_m2],
                every_post_actual_m2[time11_age_m2])
cor16_m2 <- cor(every_post_AIage_m2[time12_age_m2],
                every_post_actual_m2[time12_age_m2])

every_post_cor_mx_m2 <- data.frame(Correlation=c(cor13_m2, cor14_m2, 
                                             cor15_m2, cor16_m2),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
every_post_cor_mx_m2
```

## Analysis (Part 20.2)
```{r}
AIage_m4_m2 <- lm(every_post_AIage_m2 ~ 
                            every_post_actual_m2)
ip_m4_m2 <- influencePlot(AIage_m4_m2)
ip_m4_m2
4/length(every_post_actual_m2) # Hat-values limit for Influcence Plot
# High Leverage Points: 27, 28 (? > 4/n for Hat-values)
# Outlier Points: 13, 46 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 27, 28 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 21.2)
```{r}
# Finding the Correlation Cofficients for ALL "post-measures" for AI M2
every_post_cor_old_m2 <- cor(every_post_AIage_m2, 
                            every_post_actual_m2)

every_post_cor_compare_m2 <- data.frame(Correlation=c(every_post_cor_old_m2),
                             Type=c("All Points"))
every_post_cor_compare_m2 # No Bad Leverage Points

# Run the Linear Regression
every_all_post_m1_m2 <- lm(every_post_AIage_m2 ~
                                 every_post_actual_m2)
summary(every_all_post_m1_m2)

every_all_post_r_compare_m2 <- data.frame(R_sq=c(summary(every_all_post_m1_m2)$r.squared),
                             Type=c("All Points")) 
every_all_post_r_compare_m2 # No Bad Leverage Points
```



# Testing Reliability for ALL Combinations of "post-measurements" [AI Model 3]

**NOTE:** The parts are as follows...
  i) "post" & "post_2" are Parts 1.3 - 6.3
  ii) "post" & "post_3" are Parts 7.3 - 11.3
  iii) "post_2" & "post_3" are Parts 12.3 - 16.3
  iv) Every "post-measurement" are Parts 17.3 - 21.3

## Analysis (Part 1.3)
```{r}
## Re-order the dataset
nrow(d)
for (i in 1:301) {
  if(d$patient_name[i] %in% d$patient_name[i+1])
  {
    if(d$pre_or_post_operation[i] %in% "post_2" &&
       d$pre_or_post_operation[i+1] %in% "post")
    {
      temp <- d[i,]
      d[i,] <- d[i+1,]
      d[i+1,] <- temp
    }
  }
}
```

## Analysis (Part 2.3)
```{r, warning=FALSE, message=FALSE}
age11_m3 <- which(d$pre_or_post_operation %in% "post")
age2_m3 <- which(d$pre_or_post_operation %in% "post_2")
age3_m3 <- which(d$pre_or_post_operation %in% "post_3")
all_post_m3 <- sort(c(age11_m3, age2_m3 ,age3_m3))
age1_m3 <- age2_m3 - 1

age2_post_m3 <- d$ai_model_3[age2_m3]
age1_post_m3 <- d$ai_model_3[age1_m3]
age3_post_m3 <- d$ai_model_3[age3_m3]
post1.2_diff_m3 <- d$age_actual[age2_m3] - d$age_actual[age1_m3]
hist(post1.2_diff_m3)
```

## Analysis (Part 3.3)
```{r}
## Compute the coefficient of correlation of two postdicted age for "post" & "post_2" for AI M3
all_post1.2_index_m3 <- sort(c(age1_m3, age2_m3))
length(all_post1.2_index_m3)/2
AIage_post_m3 <- numeric(24)
AIage_post2_m3 <- numeric(24)
for (i in 1:24) {
  temp <- i * 2 -1
  if(d$age_actual[all_post1.2_index_m3[temp]] > 
     d$age_actual[all_post1.2_index_m3[temp + 1]])
  {
    AIage_post_m3[i] <- d$ai_model_3[all_post1.2_index_m3[temp + 1]]
    AIage_post2_m3[i] <- d$ai_model_3[all_post1.2_index_m3[temp]]
  }
  else{
    AIage_post_m3[i] <- d$ai_model_3[all_post1.2_index_m3[temp]]
    AIage_post2_m3[i] <- d$ai_model_3[all_post1.2_index_m3[temp + 1]]
  }
}
```

## Analysis (Part 4.3)
```{r}
post1.2_age_mx_m3 <- cbind(post1.2_diff_m3, age2_post_m3 - age1_post_m3)
post1.2_age_mx_m3 # might be better to look at head(...) and tail(...)
# Make subgroups for time
## Over Half Years & Over Full Years
time1_age_m3 <- c(which(post1.2_diff_m3 > 0.5),
                    which(post1.2_diff_m3 < -0.5))
time1_age_m3 <- sort(time1_age_m3)

time2_age_m3 <- which(post1.2_diff_m3 >= -1 & 
              post1.2_diff_m3 <= 1)
time2_age_m3 <- sort(time2_age_m3)

time3_age_m3 <- c(which(post1.2_diff_m3 < -1),
        which(post1.2_diff_m3 > 1))
time3_age_m3 <- sort(time3_age_m3)

# Correlations
cor1_m3 <- cor(AIage_post_m3, AIage_post2_m3)
cor2_m3 <- cor(AIage_post_m3[time1_age_m3], AIage_post2_m3[time1_age_m3])
cor3_m3 <- cor(AIage_post_m3[time2_age_m3], AIage_post2_m3[time2_age_m3])
cor4_m3 <- cor(AIage_post_m3[time3_age_m3], AIage_post2_m3[time3_age_m3])

post1.2_cor_mx_m3 <- data.frame(Correlation=c(cor1_m3, cor2_m3, 
                                             cor3_m3, cor4_m3),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
post1.2_cor_mx_m3
```

## Analysis (Part 5.3)
```{r}
AIage_m1_m3 <- lm(AIage_post_m3 ~ AIage_post2_m3)
ip_m1_m3 <- influencePlot(AIage_m1_m3)
ip_m1_m3
4/length(AIage_post_m3) # Hat-values limit for Influcence Plot
# High Leverage Points: N/A (? > 4/n for Hat-values)
# Outlier Points: 7, 16 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: N/A (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 6.3)
```{r}
# Finding the Correlation Cofficients for "post" & "post_2" for AI M3
post1.2_cor_old_m3 <- cor(age1_post_m3, age2_post_m3)

post1.2_cor_compare_m3 <- data.frame(Correlation=c(post1.2_cor_old_m3),
                             Type=c("All Points"))
post1.2_cor_compare_m3 # No Bad Leverage Points

# Run the Linear Regression
post1.2_all_m1_m3 <- lm(age1_post_m3 ~ age2_post_m3)
summary(post1.2_all_m1_m3)

post1.2_r_compare_m3 <- data.frame(R_sq=c(summary(post1.2_all_m1_m3)$r.squared),
                             Type=c("All Points")) 
post1.2_r_compare_m3 # No Bad Leverage Points
```

## Analysis (Part 7.3)
```{r}
# Set up data for "post" & "post_3" for AI M3
post1.3_m3 <- age3_m3 - 2
post1.3_df <- d[sort(c(post1.3_m3, age3_m3)),]
post1_m3 <- which(post1.3_df$pre_or_post_operation %in% "post")
post3_m3 <- which(post1.3_df$pre_or_post_operation %in% "post_3")

# Note: Last year's messed up and had c(1,3,5,7,9,11,14,16,18) -> "post", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "post_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
post1_df_m3 <- post1.3_df[post1_m3,] 
post3_df_m3 <- post1.3_df[post3_m3,]
```

## Analysis (Part 8.3)
```{r}
post1.3_diff_m3 <- post3_df_m3$age_actual - post1_df_m3$age_actual
post1_AIage_m3 <- post1_df_m3$ai_model_3
post3_AIage_m3 <- post3_df_m3$ai_model_3
hist(post1.3_diff_m3)
```

## Analysis (Part 9.3)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time4_age_m3 <- c(which(post1.3_diff_m3 > 0.5),
                    which(post1.3_diff_m3 < -0.5))
time4_age_m3 <- sort(time4_age_m3)

time5_age_m3 <- which(post1.3_diff_m3 >= -1 & 
              post1.3_diff_m3 <= 1)
time5_age_m3 <- sort(time5_age_m3)

time6_age_m3 <- c(which(post1.3_diff_m3 < -1),
        which(post1.3_diff_m3 > 1))
time6_age_m3 <- sort(time6_age_m3)

# Correlations
cor5_m3 <- cor(post1_AIage_m3, post3_AIage_m3)
cor6_m3 <- cor(post1_AIage_m3[time4_age_m3], post3_AIage_m3[time4_age_m3])
cor7_m3 <- cor(post1_AIage_m3[time5_age_m3], post3_AIage_m3[time5_age_m3])
cor8_m3 <- cor(post1_AIage_m3[time6_age_m3], post3_AIage_m3[time6_age_m3])

post1.3_cor_mx_m3 <- data.frame(Correlation=c(cor5_m3, cor6_m3, 
                                             cor7_m3, cor8_m3),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
post1.3_cor_mx_m3
```

## Analysis (Part 10.3)
```{r}
AIage_m2_m3 <- lm(post1_AIage_m3 ~ post3_AIage_m3)
ip_m2_m3 <- influencePlot(AIage_m2_m3)
ip_m2_m3
4/length(post1_AIage_m3) # Hat-values limit for Influcence Plot
# High Leverage Points: N/A (? > 4/n for Hat-values)
# Outlier Points: 5 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: N/A (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 11.3)
```{r}
# Finding the Correlation Cofficients for "post" & "post_3" for AI M3
post1.3_cor_old_m3 <- cor(post1_AIage_m3, post3_AIage_m3)

post1.3_cor_compare_m3 <- data.frame(Correlation=c(post1.3_cor_old_m3),
                             Type=c("All Points"))
post1.3_cor_compare_m3 # No Bad Leverage Points

# Run the Linear Regression
post1.3_all_m1_m3 <- lm(post1_AIage_m3 ~ post3_AIage_m3)
summary(post1.3_all_m1_m3)

post1.3_r_compare_m3 <- data.frame(R_sq=c(summary(post1.3_all_m1_m3)$r.squared),
                             Type=c("All Points")) 
post1.3_r_compare_m3 # No Bad Leverage Points
```

## Analysis (Part 12.3)
```{r}
# Set up data for "post_2" & "post_3" for AI M3
post2.3_m3 <- age3_m3 - 1
post2.3_df <- d[sort(c(post2.3_m3, age3_m3)),]
post2_m3 <- which(post2.3_df$pre_or_post_operation %in% "post_2")
post3_m3 <- which(post2.3_df$pre_or_post_operation %in% "post_3")

# Note: Last year's messed up and had c(1,3,5,7,10,11,14,16,18) -> "post_2", BUT the actual points should be c(1,3,5,7,9,11,13,15,17); Same goes for "post_3" since they put c(2,4,6,8,10,12,13,15,17), BUT the actual points should be c(2,4,6,8,10,12,14,16,18)
post2_df_m3 <- post2.3_df[post2_m3,] 
post3_df_m3 <- post2.3_df[post3_m3,]
```

## Analysis (Part 13.3)
```{r}
post2.3_diff_m3 <- post3_df_m3$age_actual - post2_df_m3$age_actual
post2_AIage_m3 <- post2_df_m3$ai_model_3
post3_AIage_m3 <- post3_df_m3$ai_model_3
hist(post2.3_diff_m3)
```

## Analysis (Part 14.3)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time7_age_m3 <- c(which(post2.3_diff_m3 > 0.5),
                    which(post2.3_diff_m3 < -0.5))
time7_age_m3 <- sort(time7_age_m3)

time8_age_m3 <- which(post2.3_diff_m3 >= -1 & 
              post2.3_diff_m3 <= 1)
time8_age_m3 <- sort(time8_age_m3)

time9_age_m3 <- c(which(post2.3_diff_m3 < -1),
        which(post2.3_diff_m3 > 1))
time9_age_m3 <- sort(time9_age_m3)

# Correlations
cor9_m3 <- cor(post2_AIage_m3, post3_AIage_m3)
cor10_m3 <- cor(post2_AIage_m3[time7_age_m3], post3_AIage_m3[time7_age_m3])
cor11_m3 <- cor(post2_AIage_m3[time8_age_m3], post3_AIage_m3[time8_age_m3])
cor12_m3 <- cor(post2_AIage_m3[time9_age_m3], post3_AIage_m3[time9_age_m3])

post2.3_cor_mx_m3 <- data.frame(Correlation=c(cor9_m3, cor10_m3, 
                                             cor11_m3, cor12_m3),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
post2.3_cor_mx_m3 # We have N/A since either one or no points for the time given
```

## Analysis (Part 15.3)
```{r}
AIage_m3_m3 <- lm(post2_AIage_m3 ~ post3_AIage_m3)
ip_m3_m3 <- influencePlot(AIage_m3_m3)
ip_m3_m3
4/length(post3_AIage_m3) # Hat-values limit for Influcence Plot
# High Leverage Points: N/A (? > 4/n for Hat-values)
# Outlier Points: 5 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: N/A (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: N/A (? > 4/n for Hat values & outside [-2 > ? > +2])
```

## Analysis (Part 16.3)
```{r}
# Finding the Correlation Cofficients for "post_2" & "post_3" for AI M3
post2.3_cor_old_m3 <- cor(post2_AIage_m3, post3_AIage_m3)

post2.3_cor_compare_m3 <- data.frame(Correlation=c(post2.3_cor_old_m3),
                             Type=c("All Points"))
post2.3_cor_compare_m3 # No Bad Leverage Points

# Run the Linear Regression
post2.3_all_m1_m3 <- lm(post2_AIage_m3 ~ post3_AIage_m3)
summary(post2.3_all_m1_m3) # this is a fairly high reliability

post2.3_r_compare_m3 <- data.frame(R_sq=c(summary(post2.3_all_m1_m3)$r.squared),
                             Type=c("All Points")) 
post2.3_r_compare_m3 # No Bad Leverage Points
```

## Analysis (Part 17.3)
```{r, warning=FALSE, message=FALSE}
every_post_m3 <- sort(which(d$pre_or_post_operation %in% c("post", "post_2",
                                                        "post_3")))
every_post_diff_m3 <- d$age_actual[every_post_m3] - d$ai_model_3[every_post_m3]
hist(every_post_diff_m3)
```

## Analysis (Part 18.3)
```{r}
every_post_actual_m3 <- d$age_actual[every_post_m3]
every_post_AIage_m3 <- d$ai_model_3[every_post_m3]
```

## Analysis (19.3)
```{r}
# Make subgroups for time
## Over Half Years & Over Full Years
time10_age_m3 <- c(which(every_post_diff_m3 > 0.5),
                    which(every_post_diff_m3 < -0.5))
time10_age_m3 <- sort(time10_age_m3)

time11_age_m3 <- which(every_post_diff_m3 >= -1 & 
              every_post_diff_m3 <= 1)
time11_age_m3 <- sort(time11_age_m3)

time12_age_m3 <- c(which(every_post_diff_m3 < -1),
        which(every_post_diff_m3 > 1))
time12_age_m3 <- sort(time12_age_m3)

# Correlations
cor13_m3 <- cor(every_post_AIage_m3, 
                every_post_actual_m3)
cor14_m3 <- cor(every_post_AIage_m3[time10_age_m3],
                every_post_actual_m3[time10_age_m3])
cor15_m3 <- cor(every_post_AIage_m3[time11_age_m3],
                every_post_actual_m3[time11_age_m3])
cor16_m3 <- cor(every_post_AIage_m3[time12_age_m3],
                every_post_actual_m3[time12_age_m3])

every_post_cor_mx_m3 <- data.frame(Correlation=c(cor13_m3, cor14_m3, 
                                             cor15_m3, cor16_m3),
                        Conditions=c("No Conditions", "Over Half Year", 
                                     "Over Full Year", "Within 1 Year"))
every_post_cor_mx_m3
```

## Analysis (Part 20.3)
```{r}
AIage_m4_m3 <- lm(every_post_AIage_m3 ~ 
                            every_post_actual_m3)
ip_m4_m3 <- influencePlot(AIage_m4_m3)
ip_m4_m3
4/length(every_post_AIage_m3) # Hat-values limit for Influcence Plot
# High Leverage Points: 26, 27, 28 (? > 4/n for Hat-values)
# Outlier Points: 26, 68, 130 (StudRes is either [-2 > ? > +2])
# Good Leverage Points: 27, 28 (? > 4/n for Hat values & within [-2 > ? > +2])
# Bad Leverage Points: 26 (? > 4/n for Hat values & outside [-2 > ? > +2])
lev_m4_m3 <- d[which(d$pre_or_post_operation %in% c("post","post_2","post_3")),]
lev_m4_m3[26, c(6,7,10)] # (might remove this Bad Leverage)
# We'll see what happens when we remove the Bad Leverage...
```

## Analysis (Part 21.3)
```{r}
# Finding the Correlation Cofficients for ALL "post-measures" for AI M3
every_post_cor_old_m3 <- cor(every_post_AIage_m3, 
                            every_post_actual_m3)
every_post_cor_improved_m3 <- cor(every_post_AIage_m3[-c(26)], 
                            every_post_actual_m3[-c(26)])

every_post_cor_compare_m3 <- data.frame(Correlation=c(every_post_cor_old_m3,
                                                every_post_cor_improved_m3),
                             Type=c("All Points", "Removed Bad Leverages"))
every_post_cor_compare_m3 # Removing the Bad Leverage Points (points 26) improves the reliability

# Run the Linear Regression
every_all_post_m1_m3 <- lm(every_post_actual_m3 ~
                                 every_post_AIage_m3)
summary(every_all_post_m1_m3)

every_improved_post_m1_m3 <- lm(every_post_actual_m3[-c(26)] ~
                                 every_post_AIage_m3[-c(26)])
summary(every_improved_post_m1_m3)


every_all_post_r_compare_m3 <- data.frame(R_sq=c(summary(every_all_post_m1_m3)$r.squared,
                  summary(every_improved_post_m1_m3)$r.squared),
                             Type=c("All Points", "Removed Bad Leverages")) 
every_all_post_r_compare_m3 # R-Squared improved slightly

# Conclusion: It might be better to not remove the Bad Leverage Point 26 for Model 3. By observation, it approcimately was off by 10 years. This is for comparing ALL "pre-meausres" ONLY!
lev_m4_m3[26, c(6,7,10)] # No big difference on results when removed!
as.numeric(lev_m4_m3[51, 7] - lev_m4_m3[51, 10]) # How much it was off by
```



# post-Measurements Table
## Model 1
```{r}
post_table_m1 <- matrix(nrow=4, ncol=5, byrow=TRUE,
                       c(cor1_m1,cor2_m1,cor3_m1,cor4_m1,
                         NA,
                         cor5_m1,cor6_m1,cor7_m1,cor8_m1,
                         NA,
                         cor9_m1,cor10_m1,cor11_m1,cor12_m1,
                         NA,
                         cor13_m1, cor14_m1, cor15_m1, cor16_m1,
                         NA))
rownames(post_table_m1) <- c("post1 - post2", "post1 - post3", "post2 - post3",
                            "All post-Measures")
colnames(post_table_m1) <- c("No Conditions", "0.5 < Age_Diff < -0.5", 
                                     "1 < Age_Diff < -1", 
                            "-1 < Age_Diff < 1", "Removed Bad Leverage(s)")

# c("No Conditions", "Over Half Year", "Over Full Year", "Within 1 Year", "Removed Bad Leverage(s)) -> translation for what the conditions mean above
post_table_m1
```

## Model 2
```{r}
post_table_m2 <- matrix(nrow=4, ncol=5, byrow=TRUE,
                       c(cor1_m2,cor2_m2,cor3_m2,cor4_m2,
                         NA,
                         cor5_m2,cor6_m2,cor7_m2,cor8_m2,
                         NA,
                         cor9_m2,cor10_m2,cor11_m2,cor12_m2,
                         NA,
                         cor13_m2, cor14_m2, cor15_m2, cor16_m2,
                         NA))
rownames(post_table_m2) <- c("post1 - post2", "post1 - post3", "post2 - post3",
                            "All post-Measures")
colnames(post_table_m2) <- c("No Conditions", "0.5 < Age_Diff < -0.5", 
                                     "1 < Age_Diff < -1", 
                            "-1 < Age_Diff < 1", "Removed Bad Leverage(s)")

# c("No Conditions", "Over Half Year", "Over Full Year", "Within 1 Year", "Removed Bad Leverage(s)) -> translation for what the conditions mean above
post_table_m2
```

## Model 3
```{r}
post_table_m3 <- matrix(nrow=4, ncol=5, byrow=TRUE,
                       c(cor1_m3,cor2_m3,cor3_m3,cor4_m3,
                         NA,
                         cor5_m3,cor6_m3,cor7_m3,cor8_m3,
                         NA,
                         cor9_m3,cor10_m3,cor11_m3,cor12_m3,
                         NA,
                         cor13_m3, cor14_m3, cor15_m3, cor16_m3,
                         every_post_cor_improved_m3))
rownames(post_table_m3) <- c("post1 - post2", "post1 - post3", "post2 - post3",
                            "All post-Measures")
colnames(post_table_m3) <- c("No Conditions", "0.5 < Age_Diff < -0.5", 
                                     "1 < Age_Diff < -1", 
                            "-1 < Age_Diff < 1", "Removed Bad Leverage(s)")

# c("No Conditions", "Over Half Year", "Over Full Year", "Within 1 Year", "Removed Bad Leverage(s)) -> translation for what the conditions mean above
post_table_m3

# Interestingly enough, for all of Model 3's "post-Measures" and its combinations, it was the only one with Bad Leverage Point.
```







# Accuracy for Each "post-Measures"
## Set up for showing the comparisons for each Models
```{r}
# Model 1
post1.2_MSE_m1 <- mean((post1.2_all_m1_m1$residuals)^2)
post1.3_MSE_m1 <- mean((post1.3_all_m1_m1$residuals)^2)
post2.3_MSE_m1 <- mean((post2.3_all_m1_m1$residuals)^2)
post_every_MSE_m1 <- mean((every_all_post_m1_m1$residuals)^2)


# Model 2
post1.2_MSE_m2 <- mean((post1.2_all_m1_m2$residuals)^2)
post1.3_MSE_m2 <- mean((post1.3_all_m1_m2$residuals)^2)
post2.3_MSE_m2 <- mean((post2.3_all_m1_m2$residuals)^2)
post_every_MSE_m2 <- mean((every_all_post_m1_m2$residuals)^2)


# Model 3
post1.2_MSE_m3 <- mean((post1.2_all_m1_m3$residuals)^2)
post1.3_MSE_m3 <- mean((post1.3_all_m1_m3$residuals)^2)
post2.3_MSE_m3 <- mean((post2.3_all_m1_m3$residuals)^2)
post_every_MSE_m3 <- mean((every_all_post_m1_m3$residuals)^2)
post_improved_every_MSE_m3 <- mean((every_improved_post_m1_m3$residuals)^2)


# Show the differences amongst the Models for MSE (Numerically)
post_MSE_m1 <- data.frame(Combination=c("post - post2", "post - post3",
                                       "post2 - post3"),
                         MSE=c(post1.2_MSE_m1, post1.3_MSE_m1,
                               post2.3_MSE_m1, post_every_MSE_m1))

post_MSE_m2 <- data.frame(Combination=c("post - post2", "post - post3",
                                       "post2 - post3"),
                         MSE=c(post1.2_MSE_m2, post1.3_MSE_m2,
                               post2.3_MSE_m2, post_every_MSE_m2))

post_MSE_m3 <- data.frame(Combination=c("post - post2", "post - post3",
                                       "post2 - post3", "All post-Measures",
                                       "Removed Bad Leverage(s) - All post"),
                         MSE=c(post1.2_MSE_m3, post1.3_MSE_m3,
                               post2.3_MSE_m3, post_every_MSE_m3,
                               post_improved_every_MSE_m3))


post_MSE_all <- data.frame(Combination=c("post - post2", "post - post3",
                                       "post2 - post3", "All post-Measures",
                                       "Removed Bad Leverage(s): All post"),
                          `MSE Model 1`=c(post1.2_MSE_m1, post1.3_MSE_m1,
                               post2.3_MSE_m1, post_every_MSE_m1, NA),
                         `MSE Model 2`=c(post1.2_MSE_m2, post1.3_MSE_m2,
                               post2.3_MSE_m2, post_every_MSE_m2, NA),
                         `MSE Model 3`=c(post1.2_MSE_m3, post1.3_MSE_m3,
                               post2.3_MSE_m3, post_every_MSE_m3,
                               post_improved_every_MSE_m3))

```

## Show the comparisons for each Models (Numerical)
```{r}
post_MSE_m1
post_MSE_m2
post_MSE_m3
post_MSE_all
```
