---
title: "Stats_C183_Project_3_Charles_Liu"
author: "Charles Liu (304804942)"
date: "4/25/2020"
output: pdf_document
---
Access the following data:
http://www.stat.ucla.edu/~nchristo/statistics_c183_c283/statc183c283_5stocks.txt.
In R you can access the data from the command line as follows:
a <- read.table("http://www.stat.ucla.edu/~nchristo/statistics_c183_c283/statc183c283_5stocks.txt", header=T) These are close monthly prices from January 1986 to December 2003. The first column is the date and P1; P2; P3; P4; P5 represent the close monthly prices for the stocks Exxon-Mobil, General Motors, Hewlett Packard, McDonalds, and Boeing respectively.



# a)
Convert the prices into returns for all the 5 stocks.
```{r}
a <- read.table("http://www.stat.ucla.edu/~nchristo/statistics_c183_c283/statc183c283_5stocks.txt", header=T)

r1 <- (a$P1[-length(a$P1)]-a$P1[-1])/a$P1[-1]
r2 <- (a$P2[-length(a$P2)]-a$P2[-1])/a$P2[-1]
r3 <- (a$P3[-length(a$P3)]-a$P3[-1])/a$P3[-1]
r4 <- (a$P4[-length(a$P4)]-a$P4[-1])/a$P4[-1]
r5 <- (a$P5[-length(a$P5)]-a$P5[-1])/a$P5[-1]

# And then you can create a data frame with the retuns:
returns <- as.data.frame(cbind(r1,r2,r3,r4,r5))
```



# b)
Compute the mean return for each stock and the variance-covariance matrix.
```{r}
means <- colMeans(returns)
covmat <- cov(returns)

# Values for the Means and Covmat for all Stocks:
means
covmat
```



# c)
Use only Exxon-Mobil and Boeing stocks: For these 2 stocks and the composition, expected return, and standard deviation of the minimum risk portfolio.
```{r}
means_b <- colMeans(returns[c(-2,-3,-4)]) # only Exxon-Mobil and Boeing stocks
covmat_b <-cov(returns[c(-2,-3,-4)]) # only Exxon-Mobil and Boeing stocks
ones_b <- rep(1, 2)

R_min_b <- (t(ones_b) %*% solve(covmat_b) %*% means_b)/(t(ones_b) %*% solve(covmat_b) %*% ones_b)
sigma_min_b <- (1)/((t(ones_b) %*% solve(covmat_b) %*% ones_b)^1/2)
X_b <- (solve(covmat_b) %*% ones_b)/as.integer(t(ones_b) %*% solve(covmat_b) %*% ones_b)

# Minumu Risk Portfolio for only Exxon-Mobil and Boeing stocks (composition, expected return, and standard deviation):
X_b
R_min_b
sigma_min_b
```



# d)
Plot the portfolio possibilities curve and identify the efficient frontier on it.
```{r, warning = FALSE}
A <- t(ones_b) %*% solve(covmat_b) %*% means_b
B <- t(means_b) %*% solve(covmat_b) %*% means_b
C <- t(ones_b) %*% solve(covmat_b) %*% ones_b
D <- B * C - A^2

# Hyperbola:
plot(0, A/C, main = "Portfolio Possibilities Curve", xlab = "Risk (standard deviation)",
     ylab = "Expected Return", type = "n",
     xlim = c(-2*sqrt(1/C), 4*sqrt(1/C)), 
     ylim = c(-2*A/C, 4*A/C))

# Plot center of the hyperbola:
points(0, A/C, pch = 19)

# Plot transverse and conjugate axes:
abline(v = 0) # Also this is the y-axis.
abline(h = A/C)

# Plot the x-axis:
abline(h = 0)

# Plot the minimum risk portfolio:
points(sqrt(1/C), A/C, pch=19)

# Find the asymptotes:
V <- seq(-1, 1, 0.001)
A1 <- A/C + V * sqrt(D/C)
A2 <- A/C - V * sqrt(D/C)
points(V, A1, type = "l")
points(V, A2, type = "l")

# Efficient frontier:
minvar_b <- 1/C
minE_b <- A/C
sdeff <- seq((minvar_b)^0.5, 1, by = 0.0001)
options(warn = -1)
y1 <- (A + sqrt(D*(C*sdeff^2 - 1)))*(1/C) 
y2 <- (A - sqrt(D*(C*sdeff^2 - 1)))*(1/C) 
options(warn = 0)

# The green is the Efficient Frontier
# The red is part of the Frontier
points(sdeff, y1, type = "l", col = "green")
points(sdeff, y2, type = "l", col = "red")
legend(x = "topleft", inset = 0.001, legend = c("Efficient Frontier"), lty = 1, col = c("green"), box.lty = 1)

```



# e)
Use only Exxon-Mobil, McDonalds and Boeing stocks and assume short sales are allowed to answer the following question: For these 3 stocks compute the expected return and standard deviation for many combinations of xa; xb; xc with xa + xb + xc = 1 and plot the cloud of points. You can use the following combinations of the three stocks:
a <- read.table("http://www.stat.ucla.edu/~nchristo/datac183c283/statc183c283_abc.txt", header=T)
```{r, warning = FALSE}
a_e <- read.table("http://www.stat.ucla.edu/~nchristo/datac183c283/statc183c283_abc.txt",
header=T)

means_e <- means[c(-2, -3)] # Exxon-Mobil, McDonalds, and Boeing stocks
covmat_e <- covmat[c(-2, -3), c(-2, -3)] # Exxon-Mobil, McDonalds and Boeing stocks

expected_returns <- numeric(nrow(a_e))
sdev <- numeric(nrow(a_e))

for(i in 1:nrow(a_e)){
expected_returns[i] <- as.matrix(a_e[i,]) %*% means_e
sdev[i] <- sqrt(as.matrix(a_e[i,]) %*% covmat_e %*% t(as.matrix(a_e[i,])))
}

# Plot the Cloud of Points
plot(sdev, expected_returns, xlab = "Risk (standard deviation)", ylab = "Expected Return",
main = "Exxon-Mobil, McDonalds and Boeing Stocks
(Cloud Points)", pch = 19, cex = 0.5)

# Values for the Many Combinations Portfolio (head() only):
head(sdev)
head(expected_returns)
```



# f)
Assume Rf = 0.001 and that short sales are allowed. Find the composition, expected return and standard deviation of the portfolio of the point of tangency G and draw the tangent to the efficient frontier of question (e).
```{r, warning = FALSE}
Rf <- 0.001
R <- means_e - Rf
z <- solve(covmat_e) %*% R

# Composition of G
x <- z/sum(z)

# Expected Return of G
R_Gbar <- t(x) %*% means_e

# Standard Deviation of G
sd_G <- sqrt(t(x) %*% covmat_e %*% x)

# Slope of Point of Tangency
slope <- (R_Gbar-Rf)/sd_G

# Plot the Point of Tangency G:
plot(sdev, expected_returns, xlab = "Risk (standard deviation)", ylab = "Expected Return",
main = "Exxon-Mobil, McDonalds and Boeing stocks
(Cloud Points)", pch = 19, cex = 0.5)
lines(c(0, sd_G, 4*sd_G), c(0, R_Gbar, Rf + slope*(4*sd_G)), col = "purple")
points(sd_G, R_Gbar, col = "red", pch = 19)
text(sd_G, R_Gbar + 0.0009, "G")
points(0, Rf, pch = 19)
legend(x = "topleft", inset = 0.02, legend = c("Point of tangency G", "Slope for G"), pch = 19, lty = 1,
col = c("red", "purple"), box.lty = 1)

# Values for Composition, Expected Return, and Standard Deviation of G:
x
R_Gbar
sd_G
```



# g)
Find the expected return and standard deviation of the portfolio that consists of 60% G 40% risk free asset. Show this position on the capital allocation line (CAL).
```{r}
# Mixed Portfolio for Expected Returns and Standard Deviation:
R_mixed <- R_Gbar*0.6 + Rf*0.4
sigma_mixed <- sd_G*0.6

# Plot the Mixed and Point G:
plot(sdev, expected_returns, xlab = "Risk (standard deviation)", ylab = "Expected Return",
main = "Exxon-Mobil, McDonalds and Boeing stocks
(Cloud Points)", pch = 19, cex = 0.5)
lines(c(0, sd_G, 4*sd_G), c(0, R_Gbar, Rf + slope*(4*sd_G)), col = "purple")
points(sd_G, R_Gbar, col = "red", pch = 19)
text(sd_G, R_Gbar + 0.0009, "G")
points(0, Rf, pch = 19)
points(sigma_mixed, R_mixed, col = "blue", pch = 19)
text(sigma_mixed, R_mixed + 0.0009, "M")
legend(x = "topleft", inset = 0.01, legend = c("Point of tangency G (G)", "Mix of 60% & 40% (M)", "Slope for G"), pch = 19, lty = 1, col = c("red","blue", "purple"), box.lty = 1)

# Values for our Mixed Portfolio of 60% and 40%:
R_mixed
sigma_mixed
```



# h)
Now assume that short sales allowed but risk free asset does not exist.  

## i)
Using Rf1 = 0.001 and Rf2 = 0.002 and the composition of two portfolios A and B (tangent to the efficient frontier - you found the one with Rf1 = 0.001 in question (f)).
```{r}
# Choose two risk free rates:
Rf1 <- 0.001
Rf2 <- 0.002

# Re-label to make better sense formula-wise:
R_ibar <-  means[c(-2, -3)]
var_covar <- covmat[c(-2, -3), c(-2, -3)]

# Construct the vectors RA and RB: 
RA <- R_ibar-Rf1
RB <- R_ibar-Rf2

# Find the composition of the two portfolios A, B:
zA <- solve(var_covar) %*% RA
xA <- zA/sum(zA)
zB <- solve(var_covar) %*% RB
xB <- zB/sum(zB)

# Values for our Composition of A and B:
xA
xB
```


## ii)
Compute the covariance between portfolios A and B?
```{r}
cov_AB <- t(xA) %*% var_covar %*% xB

# Value for our Covariance between A and B:
cov_AB
```


## iii)
Use your answers to (1) and (2) to trace out the efficient frontier of the stocks Exxon-Mobil, McDonalds, Boeing. Use a different color to show that the frontier is located on top of the cloud of points from question (e). Your graph should look like the one below.
```{r, warning = FALSE}
# Our composition for Portfolios A and B:
xa <- seq(-3, 5, 0.01)
xb <- 1 - xa

# Our Expected Returns from Portfolios A and B:
RA_bar <- t(xA) %*% R_ibar
RB_bar <- t(xB) %*% R_ibar

# Our Variances from Portfolios A and B:
var_A <- t(xA) %*% var_covar %*% xA
var_B <- t(xB) %*% var_covar %*% xB

# Portfolios A and B's sigma_p and rp_bar:
sigma_p <- sqrt(xa^2*var_A + xb^2*var_B+ 2*xa*xb*cov_AB)
rp_bar <- xa*RA_bar + xb*RB_bar


# Plot all below:
plot(sdev, expected_returns, xlab = "Risk (standard deviation)", ylab = "Expected Return",
main = "Portfolio Possibilites Curve of Exxon-Mobil, McDonalds and Boeing", pch = 19, cex = 0.5)
points(sigma_p, rp_bar, col = "green", cex = 0.5)
```


## iv)
Find the composition of the minimum risk portfolio (how much of each stock) and its expected return, and standard deviation.
```{r}
# Create our set of ones vector:
ones <- rep(1,3)

# Composition of Minimum Risk Portfolio:
x_min <- (solve(covmat_e) %*% ones)/as.integer(t(ones) %*% solve(covmat_e) %*% ones)

# Expected Return of Minimum Risk Portfolio:
R_min <- (t(ones) %*% solve(covmat_e) %*% as.matrix(means_e))/as.integer(t(ones) %*% solve(covmat_e) %*% ones)

# Standard Deviation of minimum risk portfolio
sigma_min <- (1)/ sqrt(t(ones) %*% solve(covmat_e) %*% ones)

# Values for Our Minimum Risk Portfolio (Compositon, Exepected Returns, Standard Deviation):
x_min
R_min
sigma_min
```