---
title: "DataExplore"
output: pdf_document
---

# Load packages
```{r, message=F}
library(tidyverse)
library(caret)
library(corrplot)
library(gridExtra) # grid.arrange
```

# 1a) Load Data
```{r,message=F}
train <- read_csv('training.csv')
test <- read_csv('test.csv')
samp <- read_csv('sample.csv')
```

# 1d) Check for NA - none
```{r}
# sum(is.na(train))
```

#1c) Some Ft. Engineering
```{r}
# split PubDate into date and time
train <- train %>% separate(PublishedDate,c("PublishedDate","PublishedTime"),sep = " ")
test <- test %>% separate(PublishedDate,c("PublishedDate","PublishedTime"),sep = " ")
train$PublishedDate <- strptime(train$PublishedDate, "%m/%d/%Y")
train$PublishedTime <- strptime(train$PublishedTime, "%H:%M")
test$PublishedDate <- strptime(test$PublishedDate, "%m/%d/%Y")
test$PublishedTime <- strptime(test$PublishedTime, "%H:%M")
# head(train)
# head(test)
# head(samp)
```

```{r}
# rating from 0 to 10
range(samp$growth_2_6) 
# dates range from 4/11 to 9/1
range(train$PublishedDate)
range(train$PublishedTime)
range(test$PublishedDate)
range(test$PublishedTime)
# dims
dim(train)
dim(test)
```

## Create numeric ver. of Pub Date and Pub Time (days since first and mins since midnight)
```{r}
# arithmetic converts date to seconds
DaysSince1 <- as.integer(train$PublishedDate - min(train$PublishedDate))/86400 # store as days
train <- cbind(DaysSince1,train)
MinsSince1 <- as.integer(train$PublishedTime - min(train$PublishedTime))/60 # store as minutes
train <- cbind(MinsSince1,train)
DaysSince1 <- as.integer(test$PublishedDate - min(test$PublishedDate))/86400 # store as days
test <- cbind(DaysSince1,test)
MinsSince1 <- as.integer(test$PublishedTime - min(test$PublishedTime))/60 # store as minutes
test <- cbind(MinsSince1,test)

# head(train)
```

```{r}
# glimpse(train)# all data are numeric except PublishedDate
```


```{r}
# first remove id and non-numeric dates
num_train <- train[,-c(3,4,5)]
dim(num_train)
# also some variables are all 0, only keep those that are not all 0
num_train <-num_train[,colSums(num_train) != 0]
dim(num_train)
# remove min and max colors, all 0 or 255, only nead mean
```

```{r}
# write.csv(num_train,"num_preds.csv", row.names = FALSE)
```

# 2) Get corr matrix for numeric data
```{r}
multicorr <- cor(num_train, use="complete.obs") # corr matrix between all predictors
sum(is.na(multicorr))
dim(multicorr)

all_mc <- as.vector(multicorr)
ggplot() + geom_histogram(aes(x=all_mc))
```

```{r}
# remove predictors with correlation with e/o above 0.75?
keep <- rowSums(abs(multicorr) >= 0.75) <= 1 # 1 because each row has the = 1 corr with self
n_keep <- rowSums(abs(multicorr) >= 0.75) > 1
uncorr <- multicorr[keep,keep] 
dim(uncorr) 
colinear <- multicorr[c(head(n_keep,-1),T),c(head(n_keep,-1),T)] # include growth to see which high corr vars to keep
dim(colinear) # removed 126
```



# 3) Subset selection

## check which have highest corr with growth
```{r}
# highest corr among all preds
multicorr_p <- multicorr[,248] %>% data.frame() %>% arrange(desc(abs(.)))
# highest corr among <= 0.75 corr preds
uncorr_p <- uncorr[,122] %>% data.frame() %>% arrange(desc(abs(.)))
# highest corr among > 0.75 corr preds
colinear_p <- colinear[,127] %>% data.frame() %>% arrange(desc(abs(.)))
```

## make corr plot among top 6 colinear vars
```{r}
top6 <- colinear %>% data.frame() %>%  arrange(desc(abs(growth_2_6))) %>% head(7) %>% rownames()
corrplot.mixed(colinear[top6,top6]) # choose cnn 17, cnn 89, and num_chars (drop cnn 12, cnn 25, and num_words)
```

Initial guess at predictors: 
Num_Views_Base_mid_high + avg_growth_low + avg_growth_low_mid + count_vids_mid_high + doc2vec_17 + Num_Views_Base_low + Num_Subscribers_Base_mid_high + num_uppercase_chars	+ Num_Views_Base_low_mid + cnn_17 + cnn_89 + num_chars