---
title: "kaggle funcs"
author: "Cassandra Tai"
date: "11/5/2020"
output: pdf_document
---

## Load necessary libraries
```{r, warning = FALSE, message = FALSE}
#library(ggplot2)
library(dplyr)
#library(reshape2)
#library(caret)
library(boot)
#library(readxl)
library(MASS) # for LDA and QDA
library(nnet) #for more than 2 response values logistic
```

##set working directory 
```{r}
setwd("C:\\Users\\cassa\\Documents\\UCLA\\Fourth Year\\Stats 101C\\Midterm Project") #change it to your own!
```

## Read in data
```{r}
data <- read.csv("training.csv", header = TRUE)
test <- read.csv("test.csv", header = TRUE) 

dim(data)

#attach(data)
#convertclass to factor
#tags <- c("NG","OG","TsG")[as.integer(data$class) + 1]
#data$classfactor <- factor(tags, levels=c("NG","OG","TsG"))
```

## Getting rid of outliers
```{r}
predictors <- c("H3K79me2_height", "N_LOF", "VEST_score","BioGRID_log_degree", "H3Kme2_height", "One_Minus_S50_score_replication_timing","ncGERP","Frameshift_indel_fraction")
NG <- data[which(data$class == 0),]
OG <- data[which(data$class == 1),]
TSG <- data[which(data$class == 2),]
##For NG
above <- which(NG$H3K79me2_height > quantile(NG$H3K79me2_height,.75)[[1]] + 1.5*IQR(NG$H3K79me2_height))
#below <- which(NG$H3K79me2_height < quantile(NG$H3K79me2_height,.25)[[1]] - 1.5*IQR(NG$H3K79me2_height))
NG <- NG[-c(above),]
below <- which(NG$H3K4me2_width > quantile(NG$H3K4me2_width,.75)[[1]] + 2*IQR(NG$H3K4me2_width))
#below <- which(TSG$H3Kme2_height < quantile(TSG$H3Kme2_height,.25)[[1]] - 1.5*IQR(TSG$H3Kme2_height))
above <- which(NG$N_LOF > quantile(NG$N_LOF,.75)[[1]] + 1.5*IQR(NG$N_LOF))
NG <- NG[-c(above,below),]

#above <- which(NG$N_LOF > quantile(NG$N_LOF,.75)[[1]] + 1.5*IQR(NG$N_LOF))
#below <- which(NG$N_LOF < quantile(NG$N_LOF,.25)[[1]] - 1.5*IQR(NG$N_LOF))

#NG <- NG[-c(above),]

above <- which(NG$VEST_score > quantile(NG$VEST_score,.75)[[1]] + 2*IQR(NG$VEST_score))
#below <- which(NG$VEST_score < quantile(NG$VEST_score,.25)[[1]] - 1.5*IQR(NG$VEST_score))

NG <- NG[-c(above),]

#above <- which(NG$Inactivating_mutations_fraction > quantile(NG$Inactivating_mutations_fraction,.75)[[1]] + 2*IQR(NG$Inactivating_mutations_fraction))
#below <- which(NG$Inactivating_mutations_fraction < quantile(NG$Inactivating_mutations_fraction,.25)[[1]] - 1.5*IQR(NG$Inactivating_mutations_fraction))
#above <- which(NG$ncGERP > quantile(NG$ncGERP,.75)[[1]] + 2*IQR(NG$ncGERP))
#NG <- NG[-c(above),]

#above <- which(NG$Frameshift_indel_fraction > quantile(NG$Frameshift_indel_fraction,.75)[[1]] + 2.5*IQR(NG$Frameshift_indel_fraction))
#below <- which(NG$Frameshift_indel_fraction < quantile(NG$Frameshift_indel_fraction,.25)[[1]] - 2.5*IQR(NG$Frameshift_indel_fraction))

#NG <- NG[-c(above,below),]

#For OG
above <- which(OG$H3K79me2_height > quantile(OG$H3K79me2_height,.75)[[1]] + 1.5*IQR(OG$H3K79me2_height))
below <- which(OG$H3K79me2_height < quantile(OG$H3K79me2_height,.25)[[1]] - 1.5*IQR(OG$H3K79me2_height))

OG <- OG[-c(above,below),]

#above <- which(OG$N_LOF > quantile(OG$N_LOF,.75)[[1]] + 1.5*IQR(OG$N_LOF))
#below <- which(OG$N_LOF < quantile(OG$N_LOF,.25)[[1]] - 1.5*IQR(OG$N_LOF))

#OG <- OG[-c(above,below),]

#above <- which(OG$VEST_score > quantile(OG$VEST_score,.75)[[1]] + 1.5*IQR(OG$VEST_score))
#below <- which(OG$VEST_score < quantile(OG$VEST_score,.25)[[1]] - 1.5*IQR(OG$VEST_score))

#OG <- OG[-c(above,below),]

#above <- which(OG$Inactivating_mutations_fraction > quantile(OG$Inactivating_mutations_fraction,.75)[[1]] + 1.5*IQR(OG$Inactivating_mutations_fraction))
#below <- which(OG$Inactivating_mutations_fraction < quantile(OG$Inactivating_mutations_fraction,.25)[[1]] - 1.5*IQR(OG$Inactivating_mutations_fraction))

#OG <- OG[-c(above,below),]

#above <- which(OG$Frameshift_indel_fraction> quantile(OG$Frameshift_indel_fraction,.75)[[1]] + 1.5*IQR(OG$One_Minus_S50_score_replication_timiOG))
#below <- which(OG$Frameshift_indel_fraction < quantile(OG$Frameshift_indel_fraction,.25)[[1]] - 1.5*IQR(OG$One_Minus_S50_score_replication_timiOG))

#OG <- OG[-c(above,below),]


#For TSG
#above <- which(TSG$H3K79me2_height > quantile(TSG$H3K79me2_height,.75)[[1]] + 1.5*IQR(TSG$H3K79me2_height))
#below <- which(TSG$H3K79me2_height < quantile(TSG$H3K79me2_height,.25)[[1]] - 1.5*IQR(TSG$H3K79me2_height))
#below <- which(TSG$H3Kme2_height < quantile(TSG$H3Kme2_height,.25)[[1]] - 1.5*IQR(TSG$H3Kme2_height))
#TSG <- TSG[-c(below),]

#above <- which(TSG$N_LOF > quantile(TSG$N_LOF,.75)[[1]] + 1.5*IQR(TSG$N_LOF))
#below <- which(TSG$N_LOF < quantile(TSG$N_LOF,.25)[[1]] - 1.5*IQR(TSG$N_LOF))

#TSG <- TSG[-c(above,below),]

#above <- which(TSG$VEST_score > quantile(TSG$VEST_score,.75)[[1]] + 1.5*IQR(TSG$VEST_score))
#below <- which(TSG$VEST_score < quantile(TSG$VEST_score,.25)[[1]] - 1.5*IQR(TSG$VEST_score))

#TSG <- TSG[-c(above,below),]

#above <- which(TSG$Inactivating_mutations_fraction > quantile(TSG$Inactivating_mutations_fraction,.75)[[1]] + 1.5*IQR(TSG$Inactivating_mutations_fraction))
#below <- which(TSG$Inactivating_mutations_fraction < quantile(TSG$Inactivating_mutations_fraction,.25)[[1]] - 1.5*IQR(TSG$Inactivating_mutations_fraction))

#TSG <- TSG[-c(above,below),]

#above <- which(TSG$Frameshift_indel_fraction > quantile(TSG$Frameshift_indel_fraction,.75)[[1]] + 1.5*IQR(TSG$One_Minus_S50_score_replication_timiTSG))
#below <- which(TSG$Frameshift_indel_fraction < quantile(TSG$Frameshift_indel_fraction,.25)[[1]] - 1.5*IQR(TSG$One_Minus_S50_score_replication_timiTSG))

#TSG <- TSG[-c(above,below),]


new_data <- rbind(NG,TSG,OG)
```


## make equal partitions
```{r}
#limit <- 100
#indexNG <- sample(which(class==0))[1:limit]
#indexOG <- sample(which(class==1))[1:limit]
#indexTSG <- sample(which(class==2))[1:limit]
#train_ind <- c(indexNG,indexOG, indexTSG)
#training_train = training[train_ind, ]
#weights.train =weights[train_ind]
#training_test = training[-train_ind, ]
#weights.test =weights[-train_ind]

#data_train = data[train_ind, ]
#data_test = data[-train_ind,]
```


# Function for WCA
```{r}
get_wca <- function(pred, true)
{
  #get max score
  max_score = sum(true == 0)*1 + sum(true == 1)*20 + sum(true==2)*20
  
  #get achieved score
  score = sum((true == 0)&(pred == 0))*1 + sum((true == 1)&(pred == 1))*20+ sum((true == 2)&(pred == 2))*20
  
  #get wca
  return (score/max_score)
}
```

# Cassandra used this one: Logistic
```{r}
#logistic model
cv.fun <- function(this.fold, data){
  train <- filter(data, my.folds != this.fold)
  validate <- filter(data, my.folds == this.fold)
  total_train_points = table(train$class)[1] + 20*sum(table(train$class)[2:3]) %>%as.integer()
  model_weights<- c(ifelse(train$class == 0,1/total_train_points,20/total_train_points))
  
  lr_model = multinom(class ~ 
                  H3K79me2_height
                + N_LOF 
                + BioGRID_log_degree
                + VEST_score
                #+ RVIS_percentile
                #+ log_gene_length
                #+ Polyphen2
                + ncGERP
                + One_Minus_S50_score_replication_timing
                #+MGAentropy
                #+Broad_H3K36me3_percentage
                #+ intolerant_pNull
                #+ Gene_age
                #+Canyon_genebody_hypermethylation
                #+Inactivating_mutations_fraction
                #+Broad_H4K20me1_percentage
                #+Frameshift_indel_fraction
                #+Inactivating_mutations_fraction
                #+H3K4me2_height
                #+Gene_body_hypomethylation_in_cancer
                #+H3K4me2_width
                , data = train,
                weights = model_weights)

  
  preds = predict(lr_model, validate)
  preds = as.integer(preds)
  preds = preds-1
  testError <- table(preds, validate$class)
  #testError
  #get posterior probabilities
  #probs = predict_data$posterior
  #print(head(probs))
  wca = get_wca(preds, validate$class)
  return(wca)

}
```


#Training and validating the model (Pick one of these to run, b/c I called them all the same name )
```{r}
#logistic model
cv.fun <- function(this.fold, data){
  train <- filter(data, my.folds != this.fold)
  validate <- filter(data, my.folds == this.fold)
  total_train_points = table(train$class)[1] + 20*sum(table(train$class)[2:3]) %>%as.integer()
  model_weights<- c(ifelse(train$class == 0,1/total_train_points,20/total_train_points))
  
  lr_model = multinom(class ~ 
                  H3K79me2_height
                + N_LOF 
                + BioGRID_log_degree
                + VEST_score
                + RVIS_percentile
                , data = train,
                weights = model_weights)

  
  preds = predict(lr_model, validate)
  preds = as.integer(preds)
  preds = preds-1
  #testError <- table(preds, validate$class)

  wca = get_wca(preds, validate$class)
  return(wca)

}
```

## Re-doing exploratory Analysis with balanced dataset
```{r}
attach(training_train)
for (feat in names(training_train)[41:60])
#for (feat in vars_to_keep)
{
  if (feat != 'class')
  {
    p = ggplot(data = training_train, aes_string(classfactor, y=feat)) + 
  geom_boxplot()
    print(p)
  }
}
#S50_score_replication_timing, Exon_Cons, N_Missense, N_LOF, N_Splice
#TSG: H3K4me3_height,H3K4me2_height, H3K79me2_height, H4K20me1_width
#NG: RVIS_percentile, ncGERP
```

```{r}
#logistic model lotssss
cv.fun <- function(this.fold, data){
  train <- filter(data, my.folds != this.fold)
  validate <- filter(data, my.folds == this.fold)
  total_train_points = table(train$class)[1] + 20*sum(table(train$class)[2:3]) %>%as.integer()
  model_weights<- c(ifelse(train$class == 0,1/total_train_points,20/total_train_points))
  
  lr_model = multinom(class ~ .
                  -  Silent_KB_Ratio 
                  - N_Missense
#                  - N_LOF
                  - N_Splice
                  - Missense_KB_Ratio
                  - LOF_KB_Ratio
                  - Missense_Entropy
                  - LOF_TO_Silent_Ratio
                  - Splice_TO_Silent_Ratio
                  - Missense_TO_Silent_Ratio
#                  - Missense_Damaging_TO_Missense_Benign_Ratio
#                  - LOF_TO_Benign_Ratio
                  - Splice_TO_Benign_Ratio 
                  - Missense_TO_Benign_Ratio
                  - Missense_Damaging_TO_Benign_Ratio
                  - Polyphen2
                  - LOF_TO_Total_Ratio 
                  - Missense_TO_Total_Ratio
                  - Splice_TO_Total_Ratio
                  - LOF_TO_Missense_Ratio
                  - Silent_fraction
                  - Nonsense_fraction
                  - Missense_fraction
#                  - Recurrent_missense_fraction
#                  - Frameshift_indel_fraction
#                  - Inframe_indel_fraction
#                  - Lost_start_and_stop_fraction
#                  - Inactivating_mutations_fraction
#                  - NonSilent_TO_Silent_Ratio
#                  - log_gene_length
                  - CDS_length
#                  - CNA_deletion 
#                  - CNA_amplification
#                  - Exon_Cons
#                  - MGAentropy
#                  - S50_score_replication_timing
                  - One_Minus_S50_score_replication_timing
#                  -VEST_score
#                  -Gene_expression_Z_score
#                  -Gene_expression_Minus_Z_score
#                  -Cell_proliferation_rate_CRISPR_KD
#                    -Minus_Cell_proliferation_rate_CRISPR_KD
#                    -Super_Enhancer_percentage
#                    -BioGRID_clossness
#                    -BioGRID_log_degree
#                    -Promoter_hypermethylation_in_cancer
#                    -Promoter_hypomethylation_in_cancer
#                    -Gene_body_hypermethylation_in_cancer
#                    -Gene_body_hypomethylation_in_cancer
#                    -Canyon_genebody_hypermethylation
#                    -intolerant_pLI
#                    -intolerant_pRec
#                    -intolerant_pNull
#                    -Synonymous_Zscore
#                    -Missense_Zscore
#                    - pLOF_Zscore
#                    -dN_to_dS_ratio
#                    -GDI 
#                    -RVIS_percentile
#                    -ncRVIS
#                    -ncGERP
#                    -Gene_age
                    -FamilyMemberCount
#                    -Length_H3K4me3
#                    -Broad_H3K4me3_percentage
#                    -H3K4me3_height
#                    -H3K4me2_width
#                    -Broad_H3K4me2_percentage
#                    -Broad_H3K4me1_percentage
#                    -H3K4me1_height
#                    -H3K36me3_width
#                    -Broad_H3K36me3_percentage
#                    -H3K36me3_height
#                    -H3K27ac_width
#                    -Broad_H3K27ac_percentage
#                    -H3K27ac_height
                    -H3K27me3_width
                    -Broad_H3K27me3_percentage
                    -H3K27me3_height
                    -H3K9me3_width
                    -Broad_H3K9me3_percentage
                    -H3K9me3_height
                    -H3K9ac_width
                    -Broad_H3K9ac_percentage
                    -H3K9ac_height
                    -H3K9me2_width
                    -Broad_H3K9me2_percentage
                    -H3K9me2_height
                    -H3K79me2_width 
#                    -Broad_H4K20me1_percentage
#                    -H4K20me1_height
                    -class
                    -classfactor
                , train, weights = model_weights
                )

  
  preds = predict(lr_model, validate)
  preds = as.integer(preds)
  preds = preds-1
  #testError <- table(preds, validate$class)

  wca = get_wca(preds, validate$class)
  return(wca)

}
```

##LDA model
```{r}
#lda model
cv.fun <- function(this.fold, data){
  train <- filter(data, my.folds != this.fold)
  validate <- filter(data, my.folds == this.fold)
  #total_train_points = table(train$class)[1] + 20*sum(table(train$class)[2:3]) %>%as.integer()
  #model_weights<- c(ifelse(train$class == 0,1/total_train_points,20/total_train_points))
  
  lda.model = lda(class ~ 
                  H3K79me2_height
                + N_LOF 
                + BioGRID_log_degree
                + VEST_score
                + RVIS_percentile
                , data = train)

  
  predictions = predict(lda.model, validate)
  preds = as.integer(predictions$class)
  preds = preds-1
  #testError <- table(preds, validate$class)
  #testError

  wca = get_wca(preds, validate$class)
  return(wca)

}
```


```{r}
#lda model lots
cv.fun <- function(this.fold, data){
  train <- filter(data, my.folds != this.fold)
  validate <- filter(data, my.folds == this.fold)
  #total_train_points = table(train$class)[1] + 20*sum(table(train$class)[2:3]) %>%as.integer()
  #model_weights<- c(ifelse(train$class == 0,1/total_train_points,20/total_train_points))
  
  lda.model = lda(class ~ 
                  H3K79me2_height
                + N_LOF 
                + BioGRID_log_degree
                + VEST_score
                + RVIS_percentile
                , data = train)

  
  predictions = predict(lda.model, validate)
  preds = as.integer(predictions$class)
  preds = preds-1
  #testError <- table(preds, validate$class)
  #testError

  wca = get_wca(preds, validate$class)
  return(wca)

}
```

##QDA Model
```{r}
#qda model
cv.fun <- function(this.fold, data){
  train <- filter(data, my.folds != this.fold)
  validate <- filter(data, my.folds == this.fold)
  #total_train_points = table(train$class)[1] + 20*sum(table(train$class)[2:3]) %>%as.integer()
  #model_weights<- c(ifelse(train$class == 0,1/total_train_points,20/total_train_points))
  
  lda.model = qda(class ~ 
                  H3K79me2_height
                + N_LOF 
                + BioGRID_log_degree
                + VEST_score
                + RVIS_percentile
                , data = train)

  
  predictions = predict(lda.model, validate)
  preds = as.integer(predictions$class)
  preds = preds-1
  #testError <- table(preds, validate$class)
  #testError

  wca = get_wca(preds, validate$class)
  return(wca)

}
```


##Iterate through n iterations of k fold cv
```{r}
set.seed(1)
n = 1 #n iterations of k fold cv
for(i in 1:n) {
  #partition the data
  k = 5 #how many folds we want
  data <- mutate(new_data,
                   my.folds = sample(1:k,
                                     size = nrow(new_data),
                                     replace = TRUE))
  wca.values <- sapply(seq_len(k),
                     FUN = cv.fun,
                     data = new_data) #%>% mean()
  print(wca.values)
  print(mean(wca.values))
}
```

[1] 0.8168663 0.7539887 0.7358283 0.8134041 0.7405281
[1] 0.7721231

[1] 0.7411554 0.7645260 0.8329032 0.8435374 0.7515593
[1] 0.7867363